### 2016-08-21 TEX/draft.tex
Added .tex and .pdf files

\documentclass{report}
\usepackage[utf8]{inputenc}

\title{Report on Certificate Tools}
\author{Oliver Bodnár}
\date{August 2016}

\begin{document}

\maketitle

\tableofcontents
\newpage
\section{Overview}

\section{OpenSSL}
\subsection{type}
OpenSSL uses PKCS12 to store keys and or certificates. Certificates and keys  made in OpenSSL however are being made into PEM or DER encoded file. Said keys/certificates can then be stored inside single .pfx file made with

\subsection{Viewing stored certificates}
PEM encoded certificates (.pem|.cer|.crt):
        openssl x509 -in sample_cert.extention -text -noout

DER encoded certificates (.der):
        openssl x509 -in certificate.der -inform der -text -noout

Importing PEM or DER encoded keys or certificates into PKCS#12 file:

        openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem

        -certfile othercerts.pem option is used only if importing more certificates into 1 PKCS#12 file is wanted.

\subsection{License}
OpenSSL is free to use commercialy, however creating CA is not advised - OPENSSL O'REILY page 59 - but also hinted in manual pages - The ca command is quirky and at times downright unfriendly.

The ca utility was originally meant as an example of how to do things in a CA . It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.

The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.

\subsection{Generation of / signing a certificate}

\subsubsection{Generate keys and self-signed certificate}
It is possible to generate private key and self signed certificate with command openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt

\subsubsection{Generate keys and Certificate Signing Request}
It is possible to generate private key and CSR with command openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key

\subsubsection{Certificate Signing Request signing}
CSR signing can be done by CA created in openSSL by command
openssl ca -config ca/openssl.cnf \
      -extensions server_cert -days 375 -notext -md sha256 \
      -in ca/csr/www.example.com.csr.pem \
      -out ca/certs/www.example.com.cert.pem

\subsubsection{Create combination of private key and signed chain}
First creation of the request is needed, after that request must be signed. To combine them together the creation of pkcs#12 file is needed with commands:
        openssl pkcs12 -export -out outfilename.p12 -in signed_certificate.crt -inkey privateKey.key -chain -CAfile ca-all.crt -password pass:PASSWORD

\subsection{Specification of key length and algorithm}
Key length and algorithm is specified while generating key, currently OpenSSL supports Public-key cryptography algorithms:
RSA, DSA, Diffie-Hellman key exchange, Elliptic Curve

In the past also support for GOST R 34.10-2001 but as of January 2016 deprecated (https://mta.openssl.org/pipermail/openssl-commits/2016-January/003023.html )

\subsection{Specification of validity}
Validity is specified by CA at the moment of signing CSR.

\subsection{Basic Constraints}
Specification of constraints is made by changing basicConstraints part in [ v3_req ] part of openssl.cnf of CA
[ v3_req ]

basicConstraints=critical,CA:BOOL_VAL, pathlen:<maxChainLengthInteger>

\subsection{Seting Subject Alternative Name for end certificates}
To set SAN the change of subjectAltName in openssl.cnf is needed

[ v3_req ]
subjectAltName = @alt_names

[alt_names]
DNS.1 = example1.com
DNS.2 = example2.com
DNS.<next_number> = dns_webaddress.com

\subsection{Using Cryptographic Service Provider}
//TO DO

\subsection{Conversions}
PKCS12 and JKS conversion in OpenSSL
//AFAIK cannot be done using only OpenSSL needed to be tested/researched more

\subsection{Export certificate only from PKCS12 file}
It can be done with command:
openssl pkcs12 -in [yourfile.pfx] -clcerts -nokeys -out [certificate.crt]

\subsection{Export private key only from PKCS12 file}
To export private key use command:
openssl pkcs12 -nocerts -in [filename.pfx] -out [site.key]

\subsection{Importing certificates and private keys into PKCS12 file}
//should be possible with openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem but need to test it.

\section{Keygen}

\end{document}

### 2016-08-21 TEX/draft.tex
Changes to .tex

@@
 \newpage
-\section{Overview}
+\part{Overview}
+\chapter{Tools Overview Table}
 
-\section{OpenSSL}
-\subsection{type}
+\part{Tools}
+\chapter{OpenSSL}
+\section{type}
 OpenSSL uses PKCS12 to store keys and or certificates.
@@
 
-\subsection{Viewing stored certificates}
+\section{Viewing stored certificates}
 PEM encoded certificates (.pem|.cer|.crt):
+\begin{verbatim}
         openssl x509 -in sample_cert.extention -text -noout
+\end{verbatim}
+DER encoded certificates (.der):
+\begin{verbatim}
+        openssl x509 -in certificate.der -inform der -text -noout
+\end{verbatim}
+Importing PEM or DER encoded keys or certificates into PKCS#12 file:
+\begin{verbatim}
+        openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
+\end{verbatim}
+        certfile option is used only if importing more certificates into a single PKCS#12 file is wanted.
 
-DER encoded certificates (.der):
-        openssl x509 -in certificate.der -inform der -text -noout
-
-Importing PEM or DER encoded keys or certificates into PKCS#12 file:
-
-        openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
-
-        -certfile othercerts.pem option is used only if importing more certificates into 1 PKCS#12 file is wanted.
-
-\subsection{License}
-OpenSSL is free to use commercialy, however creating CA is not advised - OPENSSL O'REILY page 59 - but also hinted in manual pages - The ca command is quirky and at times downright unfriendly.
+\section{License}
+OpenSSL is free to use commercialy, however creating CA is not advised - OPENSSL O'REILY page 59 - but also hinted in manual pages.
+The ca command is quirky and at times downright unfriendly.
 
@@
 
-\subsection{Generation of / signing a certificate}
+\section{Generation of / signing a certificate}
 
-\subsubsection{Generate keys and self-signed certificate}
-It is possible to generate private key and self signed certificate with command openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
+\subsection{Generate keys and self-signed certificate}
+It is possible to generate private key and self signed certificate with 
+\begin{verbatim}
+openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
+\end{verbatim}
 
-\subsubsection{Generate keys and Certificate Signing Request}
-It is possible to generate private key and CSR with command openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
+\subsection{Generate keys and Certificate Signing Request}
+It is possible to generate private key and CSR with
+\begin{verbatim}
+openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
+\end{verbatim}
 
-\subsubsection{Certificate Signing Request signing}
+\subsection{Certificate Signing Request signing}
 CSR signing can be done by CA created in openSSL by command
-openssl ca -config ca/openssl.cnf \
-      -extensions server_cert -days 375 -notext -md sha256 \
-      -in ca/csr/www.example.com.csr.pem \
-      -out ca/certs/www.example.com.cert.pem
+\begin{verbatim}
+openssl ca -config ca/openssl.cnf -extensions server_cert -days 375 -notext -md sha256 -in ca/csr/www.example.com.csr.pem -out ca/certs/www.example.com.cert.pem
+\end{verbatim}
 
-\subsubsection{Create combination of private key and signed chain}
+\subsection{Create combination of private key and signed chain}
 First creation of the request is needed, after that request must be signed. To combine them together the creation of pkcs#12 file is needed with commands:
+\begin{verbatim}
         openssl pkcs12 -export -out outfilename.p12 -in signed_certificate.crt -inkey privateKey.key -chain -CAfile ca-all.crt -password pass:PASSWORD
+\end{verbatim}
 
@@
 Specification of constraints is made by changing basicConstraints part in [ v3_req ] part of openssl.cnf of CA
+\begin{verbatim}
 [ v3_req ]
 
-basicConstraints=critical,CA:BOOL_VAL, pathlen:<maxChainLengthInteger>
+basicConstraints=critical,CA:BOOL_VAL,\
+ pathlen:<maxChainLengthInteger>
+\end{verbatim}
 
@@
 To set SAN the change of subjectAltName in openssl.cnf is needed
-
+\begin{verbatim}
 [ v3_req ]
@@
 DNS.<next_number> = dns_webaddress.com
+\end{verbatim}
 
 \subsection{Using Cryptographic Service Provider}
-//TO DO
+TO DO
 
-\subsection{Conversions}
-PKCS12 and JKS conversion in OpenSSL
-//AFAIK cannot be done using only OpenSSL needed to be tested/researched more
+\section{Conversions}
+\subsection{PKCS12 and JKS conversion in OpenSSL}
 
@@
 It can be done with command:
-openssl pkcs12 -in [yourfile.pfx] -clcerts -nokeys -out [certificate.crt]
+\begin{verbatim}
+openssl pkcs12 -in yourfile.pfx -clcerts \
+ -nokeys -out certificate.crt 
+\end{verbatim}
 
@@
 To export private key use command:
-openssl pkcs12 -nocerts -in [filename.pfx] -out [site.key]
+\begin{verbatim}
+openssl pkcs12 -nocerts -in filename.pfx -out site.key
+\end{verbatim}
 
-\subsection{Importing certificates and private keys into PKCS12 file}
-//should be possible with openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem but need to test it.
+\subsection{Importing into PKCS12 file}
+should be possible with 
+\begin{verbatim}
+openssl pkcs12 -export -in file.pem -out file.p12 \
 
-\section{Keygen}
+-name "My Certificate" -certfile \
+othercerts.pem but need to test it.
+\end{verbatim}
+
+\chapter{Keygen}
 

### 2016-08-23 TEX/draft.tex
Removed OpenSSL text because something in it was making TeX unable to compile, added tables need to work on them more

--- 2016-08-21 TEX/draft.tex
@@
 \usepackage[utf8]{inputenc}
+\usepackage{multirow}
+\usepackage[table,xcdraw]{xcolor}
+\usepackage{adjustbox,lipsum}
 
@@
 \tableofcontents
+
 \newpage
-\section{Overview}
 
-\section{OpenSSL}
-\subsection{type}
-OpenSSL uses PKCS12 to store keys and or certificates.
-Certificates and keys  made in OpenSSL however are being made into PEM or DER encoded file.
-Said keys/certificates can then be stored inside single .pfx file made with
+\part{Overview}
 
-\subsection{Viewing stored certificates}
-PEM encoded certificates (.pem|.cer|.crt):
-        openssl x509 -in sample_cert.extention -text -noout
+\chapter{Overview Tables}
 
-DER encoded certificates (.der):
-        openssl x509 -in certificate.der -inform der -text -noout
+\section{General}
+\begin{table}[]
+\centering
+\caption{Overwiew General}
+\label{my-label}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
+\multirow{-2}{*}{Tools} & Type   & View + info                 & License \\ \hline
+OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
+Keygen                  & JKS    &                             &         \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
 
-Importing PEM or DER encoded keys or certificates into PKCS#12 file:
+\section{Generation and signing of certificates}
+\begin{table}[]
+\centering
+\caption{Generation and signing table}
+\label{my-label}
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+                        & \multicolumn{11}{c|}{Generation and signing}                                                                                                                                                                                                                                                                                                                                                                                                                                      \\ \cline{2-12}
+                        & \multicolumn{4}{c|}{Generate keys}                                                                                                                             &                               &                                          &                                                & \multicolumn{2}{c|}{Basic Constraints}                    &                                            &                                                                             \\ \cline{2-5} \cline{9-10}
+\multirow{-3}{*}{Tools} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & Specify Type                & Specify path length         & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
+OpenSSL                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
+Keygen                  &                                                                      &                             &                             &                             &                               &                                          &                                                &                             &                             &                                            &                                                                             \\ \hline
+                        &                                                                      &                             &                             &                             &                               &                                          &                                                &                             &                             &                                            &                                                                             \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
 
-        openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
+\part{Tools}
 
-        -certfile othercerts.pem option is used only if importing more certificates into 1 PKCS#12 file is wanted.
-
-\subsection{License}
-OpenSSL is free to use commercialy, however creating CA is not advised - OPENSSL O'REILY page 59 - but also hinted in manual pages - The ca command is quirky and at times downright unfriendly.
-
-The ca utility was originally meant as an example of how to do things in a CA . It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.
-
-The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.
-
-\subsection{Generation of / signing a certificate}
-
-\subsubsection{Generate keys and self-signed certificate}
-It is possible to generate private key and self signed certificate with command openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
-
-\subsubsection{Generate keys and Certificate Signing Request}
-It is possible to generate private key and CSR with command openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
-
-\subsubsection{Certificate Signing Request signing}
-CSR signing can be done by CA created in openSSL by command
-openssl ca -config ca/openssl.cnf \
-      -extensions server_cert -days 375 -notext -md sha256 \
-      -in ca/csr/www.example.com.csr.pem \
-      -out ca/certs/www.example.com.cert.pem
-
-\subsubsection{Create combination of private key and signed chain}
-First creation of the request is needed, after that request must be signed. To combine them together the creation of pkcs#12 file is needed with commands:
-        openssl pkcs12 -export -out outfilename.p12 -in signed_certificate.crt -inkey privateKey.key -chain -CAfile ca-all.crt -password pass:PASSWORD
-
-\subsection{Specification of key length and algorithm}
-Key length and algorithm is specified while generating key, currently OpenSSL supports Public-key cryptography algorithms:
-RSA, DSA, Diffie-Hellman key exchange, Elliptic Curve
-
-In the past also support for GOST R 34.10-2001 but as of January 2016 deprecated (https://mta.openssl.org/pipermail/openssl-commits/2016-January/003023.html )
-
-\subsection{Specification of validity}
-Validity is specified by CA at the moment of signing CSR.
-
-\subsection{Basic Constraints}
-Specification of constraints is made by changing basicConstraints part in [ v3_req ] part of openssl.cnf of CA
-[ v3_req ]
-
-basicConstraints=critical,CA:BOOL_VAL, pathlen:<maxChainLengthInteger>
-
-\subsection{Seting Subject Alternative Name for end certificates}
-To set SAN the change of subjectAltName in openssl.cnf is needed
-
-[ v3_req ]
-subjectAltName = @alt_names
-
-[alt_names]
-DNS.1 = example1.com
-DNS.2 = example2.com
-DNS.<next_number> = dns_webaddress.com
-
-\subsection{Using Cryptographic Service Provider}
-//TO DO
-
-\subsection{Conversions}
-PKCS12 and JKS conversion in OpenSSL
-//AFAIK cannot be done using only OpenSSL needed to be tested/researched more
-
-\subsection{Export certificate only from PKCS12 file}
-It can be done with command:
-openssl pkcs12 -in [yourfile.pfx] -clcerts -nokeys -out [certificate.crt]
-
-\subsection{Export private key only from PKCS12 file}
-To export private key use command:
-openssl pkcs12 -nocerts -in [filename.pfx] -out [site.key]
-
-\subsection{Importing certificates and private keys into PKCS12 file}
-//should be possible with openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem but need to test it.
-
-\section{Keygen}
+\chapter{Keygen}
 

### 2016-08-24 TEX/draft.tex
I tried to section the overview part, tommorow i will add text + finish OpenSSL text

@@
-\documentclass{report}
+\documentclass[10pt, a4paper]{report}
 \usepackage[utf8]{inputenc}
+\usepackage{booktabs}
 \usepackage{multirow}
@@
 \usepackage{adjustbox,lipsum}
+
+\setlength{\oddsidemargin}{0cm}
+\setlength{\evensidemargin}{0cm}
+\setlength{\textwidth}{500pt}
 
@@
 \section{General}
-\begin{table}[]
+%TABLE START
+\begin{table}[h!]
 \centering
@@
 \label{my-label}
-\begin{center}
+\begin{adjustbox}{max width=\textwidth}
 \begin{tabular}{|c|c|c|c|}
@@
                         & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
-\multirow{-2}{*}{Tools} & Type   & View + info                 & License \\ \hline
+\multirow{-2}{*}{Tools} & Type   & View and information        & License \\ \hline
 OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
@@
 \end{tabular}
-\end{center}
+\end{adjustbox}
 \end{table}
+%TABLE END
+
+\subsection{Type}
+Sample text for defining what Type means
+
+\subsection{View and information}
+Sample text for definition.
+
+\subsection{License}
+Sample text for definition.
+
+\newpage
 
 \section{Generation and signing of certificates}
-\begin{table}[]
+
+\subsection{Keys, certificates and basic constraints}
+%TABLE START
+\begin{table}[h!]
 \centering
-\caption{Generation and signing table}
+\caption{Generation of keys and certificates and basic constrints}
+\begin{adjustbox}{max width=\textwidth}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7}
+\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
+OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+Keygen                 &                                                                      &                             &                             &                             &                             &                             \\ \hline
+\end{tabular}
+\end{adjustbox}
+\end{table}
+%TABLE END
+
+\subsubsection{Generate keys}
+
+\paragraph{Self-signed certificate}
+Some sample text.
+
+\paragraph{Certificate Signing Request}
+More sample text.
+
+\paragraph{Specify length}
+Even more sample text.
+
+\paragraph{Specify algorithm}
+You guessed it! More sample text.
+
+\subsubsection{Basic Constraints}
+
+\paragraph{Specify Type}
+Not even trying to come up with sample text.
+
+\paragraph{Specify path length}
+Path length is long as long you wish it.
+
+\subsection{Specifications}
+
+%TABLE START
+\begin{table}[h!]
+\centering
+\caption{Specifications}
 \label{my-label}
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{adjustbox}{max width=\textwidth}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-                        & \multicolumn{11}{c|}{Generation and signing}                                                                                                                                                                                                                                                                                                                                                                                                                                      \\ \cline{2-12}
-                        & \multicolumn{4}{c|}{Generate keys}                                                                                                                             &                               &                                          &                                                & \multicolumn{2}{c|}{Basic Constraints}                    &                                            &                                                                             \\ \cline{2-5} \cline{9-10}
-\multirow{-3}{*}{Tools} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & Specify Type                & Specify path length         & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
-OpenSSL                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
-Keygen                  &                                                                      &                             &                             &                             &                               &                                          &                                                &                             &                             &                                            &                                                                             \\ \hline
-                        &                                                                      &                             &                             &                             &                               &                                          &                                                &                             &                             &                                            &                                                                             \\ \hline
+                       &                               &                                          &                                                &                                            &                                                                             \\
+\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
+OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
+Keygen                 &                               &                                          &                                                &                                            &                                                                             \\ \hline
 \end{tabular}
-\end{center}
+\end{adjustbox}
 \end{table}
+%TABLE END
+
+\paragraph{Certificate Signing Request signing}
+Some random text.
+
+\paragraph{Create combination of private key and signed chain}
+Some random text.
+
+\paragraph{Specify certificate validity}
+Some random text.
+
+\paragraph{Setting Subject Alternative Name for end certificates}
+Some random text.
+
+\paragraph{Support for Cryptographic Service Provider}
+Some random text.
+
+\newpage
+
+\section{Conversions}
+
+%TABLE START
+\begin{table}[h!]
+\centering
+\caption{Conversions}
+\label{my-label}
+\begin{adjustbox}{max width=\textwidth}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
+\multirow{-2}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
+OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+Keygen                  &                                  &                             &                                         &                                                                  \\ \hline
+                        &                                  &                             &                                         &                                                                  \\ \hline
+\end{tabular}
+\end{adjustbox}
+\end{table}
+%TABLE END
+
+\subsection{Exporting}
+
+\subsubsection{Certificate or certificate chain from a file}
+Some random text.
+
+\subsubsection{Private key only}
+Some random text.
+
+\subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+Some random text.
+
+\subsection{Importing of certificates and keys into storage files}
+Some random text.
+
+\newpage
 

### 2016-08-24 TEX/draft.tex
Added sample for next tools, trying to work out how to format code parts of text

@@
 \usepackage{adjustbox,lipsum}
+\usepackage{alltt} %for code snippets
 
@@
 \subsection{Type}
-Sample text for defining what Type means
+This section defines type of storage file in which the certificates or keys are saved. Most common are PKCS\#12 (.pfx and .p12 extentions) and JKS (Java KeyStore).
 
 \subsection{View and information}
-Sample text for definition.
+This section shows whether it is possible to view certificates or keys and additional information.
+Yes means that at least viewing is supported while not necessary meaning possibility of viewing more information about certificate.
 
 \subsection{License}
-Sample text for definition.
+Type of license and possibility of using said tool for testing or production code.
+Public means that license is not requiered for use in production code but does not mean that it should be used as such.
+Definition if it is advised to use said tool in production code or only in testing enviroment will be talked about in the next chapter under each tool.
 
@@
 \paragraph{Self-signed certificate}
-Some sample text.
+possibility of using 1 command to generate key pair and self-signed certificate
 
 \paragraph{Certificate Signing Request}
-More sample text.
+possibility of using a command to generate key pair and certificate signing request to certificate authority.
 
 \paragraph{Specify length}
-Even more sample text.
+possibility to specify the length of output key
 
 \paragraph{Specify algorithm}
-You guessed it! More sample text.
+possibility to choose between different types of algorithms for key generation
 
@@
 \paragraph{Specify Type}
-Not even trying to come up with sample text.
+specify if generated certificate will belong to certificate authority or whether it will be end certificate
 
 \paragraph{Specify path length}
-Path length is long as long you wish it.
+specify the maximum length of certificate authority chain
 
@@
 \paragraph{Certificate Signing Request signing}
-Some random text.
+possibility of signing a certificate signing request with certificate authority's key
 
 \paragraph{Create combination of private key and signed chain}
-Some random text.
+possibility of generating private key and chain signed by certificate authority that will be outputed to a single file
 
 \paragraph{Specify certificate validity}
-Some random text.
+possibility of choosing how long will the certificate be valid. This should be done by certificate authority.
 
 \paragraph{Setting Subject Alternative Name for end certificates}
-Some random text.
+possibility of choosing Subject Alternative Name for end certificates. That should be done by IP's or DNS addresses.
 
 \paragraph{Support for Cryptographic Service Provider}
-Some random text.
-
-\newpage
+whether the use, choosing and changing of Cryptographic Service Provider is supported.
 
@@
 \subsubsection{Certificate or certificate chain from a file}
-Some random text.
+Possibility of extracting certificate or certificate only from a file. Choice of Yes based on possibility of extracting either from a file.
 
 \subsubsection{Private key only}
-Some random text.
+Possibility of extracting private key from tool's file storage type of choice.
 
 \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-Some random text.
+Possibility of direct conversion (by a command of tested tool) between Java KeyStore and PKCS\#12 type file.
 
 \subsection{Importing of certificates and keys into storage files}
-Some random text.
+Possibility of importing (additional?) certificates and keys into storage files of said tool. Yes if it is possible to import or add another certificate or key into storage.
 
 \newpage
+%TOOLS PART
+\part{Tools}
 
-\part{Tools}
+%OPENSSL text added by parts, need to check commands again
+\chapter{OpenSSL}
+
+\section{General}
+
+  \subsection{Type}
+  OpenSSL uses PKCS12 to store keys and or certificates.
+Certificates and keys  made in OpenSSL however are being made into PEM or DER encoded file.
+Said keys/certificates can then be stored inside single .pfx file.
+
+  \subsection{View and information}
+
+\subsubsection{Viewing stored certificates}
+\paragraph{PEM encoded certificates (.pem$|$.cer$|$.crt):}
+
+  \verb+openssl x509 -in sample_cert.extention -text -noout+
+
+\paragraph{DER encoded certificates (.der):}
+
+  \verb+openssl x509 -in certificate.der -inform der -text -noout+
+
+\paragraph{Importing PEM or DER encoded keys or certificates into PKCS#12 file:}
+
+  \verb+openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem+
+
+certfile option is used only if importing more certificates into a single PKCS\#12 file is wanted.
+
+  \subsection{License}
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+
+      \paragraph{Certificate Signing Request}
+
+      \paragraph{Specify length}
+
+      \paragraph{Specify algorithm}
+
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+
+      \paragraph{Specify path length}
+
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+
+    \subsubsection{Support for Cryptographic Service Provider}
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+
+    \subsubsection{Private key only}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+
+  \subsection{Importing certificates and keys into storage files}
 
@@
 
+%TEMPLATE FOR ALL OTHER TOOLS
+\chapter{Tool Page Template}
+
+\section{General}
+
+  \subsection{Type}
+
+  \subsection{View and information}
+
+  \subsection{License}
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+
+      \paragraph{Certificate Signing Request}
+
+      \paragraph{Specify length}
+
+      \paragraph{Specify algorithm}
+
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+
+      \paragraph{Specify path length}
+
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+
+    \subsubsection{Support for Cryptographic Service Provider}
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+
+    \subsubsection{Private key only}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+
+  \subsection{Importing certificates and keys into storage files}
+
 \end{document}

### 2016-08-24 TEX/draft.tex
At least a little bit better code formating, to do from OPENSSL License onward (need to learn how to use citations)

@@
 \usepackage{alltt} %for code snippets
+
+\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\} %used for better formating of some text
 
@@
 \subsubsection{Viewing stored certificates}
-\paragraph{PEM encoded certificates (.pem$|$.cer$|$.crt):}
+\myparagraph{PEM encoded certificates (.pem$\vert$.cer$\vert$.crt):}
 
@@
 
-\paragraph{DER encoded certificates (.der):}
+\myparagraph{DER encoded certificates (.der):}
 
@@
 
-\paragraph{Importing PEM or DER encoded keys or certificates into PKCS#12 file:}
+\myparagraph{Importing PEM or DER encoded keys or certificates into PKCS\#12 file:}
 
@@
   \subsection{License}
+OpenSSL is free to use commercialy, however creating CA is not advised
+a) OPENSSL O'REILY page 59 
+b) hinted in manual pages.
+
+The ca command is quirky and at times downright unfriendly.
+
+The ca utility was originally meant as an example of how to do things in a CA . It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.
+
+The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.
 

### 2016-08-25 TEX/draft.tex
added old formated text to show error in compilation

@@
 Certificates and keys  made in OpenSSL however are being made into PEM or DER encoded file.
-Said keys/certificates can then be stored inside single .pfx file.
+Said keys/certificates can then be stored inside single .pfx file made with
 
-  \subsection{View and information}
+\subsection{Viewing stored certificates}
+PEM encoded certificates (.pem|.cer|.crt):
+\begin{verbatim}
+openssl x509 -in sample_cert.extention -text -noout
+\end{verbatim}
 
-\subsubsection{Viewing stored certificates}
-\myparagraph{PEM encoded certificates (.pem$\vert$.cer$\vert$.crt):}
+DER encoded certificates (.der):
+\begin{verbatim}
+openssl x509 -in certificate.der -inform der -text -noout
+\end{verbatim}
 
-  \verb+openssl x509 -in sample_cert.extention -text -noout+
-
-\myparagraph{DER encoded certificates (.der):}
-
-  \verb+openssl x509 -in certificate.der -inform der -text -noout+
-
-\myparagraph{Importing PEM or DER encoded keys or certificates into PKCS\#12 file:}
-
-  \verb+openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem+
-
-certfile option is used only if importing more certificates into a single PKCS\#12 file is wanted.
+Importing PEM or DER encoded keys or certificates into PKCS#12 file:
+\begin{verbatim}
+openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
+\end{verbatim}
+certfile option is used only if importing more certificates into a single PKCS#12 file is wanted.
 
 \subsection{License}
-OpenSSL is free to use commercialy, however creating CA is not advised
-a) OPENSSL O'REILY page 59 
-b) hinted in manual pages.
-
+OpenSSL is free to use commercialy, however creating CA is not advised - OPENSSL O'REILY page 59 - but also hinted in manual pages.
 The ca command is quirky and at times downright unfriendly.
@@
 
-\section{Generation and signing of certificates}
+\section{Generation of / signing a certificate}
 
-  \subsection{Keys, certificates and basic constraints}
+\subsection{Generate keys and self-signed certificate}
+It is possible to generate private key and self signed certificate with 
+\begin{verbatim}
+openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
+\end{verbatim}
 
-    \subsubsection{Generate keys}
+\subsection{Generate keys and Certificate Signing Request}
+It is possible to generate private key and CSR with
+\begin{verbatim}
+openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
+\end{verbatim}
 
-      \paragraph{Self-signed certificate}
+\subsection{Certificate Signing Request signing}
+CSR signing can be done by CA created in openSSL by command
+\begin{verbatim}
+openssl ca -config ca/openssl.cnf -extensions server_cert -days 375 -notext -md sha256 -in ca/csr/www.example.com.csr.pem -out ca/certs/www.example.com.cert.pem
+\end{verbatim}
 
-      \paragraph{Certificate Signing Request}
+\subsection{Create combination of private key and signed chain}
+First creation of the request is needed, after that request must be signed. To combine them together the creation of pkcs#12 file is needed with commands:
+\begin{verbatim}
+        openssl pkcs12 -export -out outfilename.p12 -in signed_certificate.crt -inkey privateKey.key -chain -CAfile ca-all.crt -password pass:PASSWORD
+\end{verbatim}
 
-      \paragraph{Specify length}
+\subsection{Specification of key length and algorithm}
+Key length and algorithm is specified while generating key, currently OpenSSL supports Public-key cryptography algorithms:
+RSA, DSA, Diffie-Hellman key exchange, Elliptic Curve
 
-      \paragraph{Specify algorithm}
+In the past also support for GOST R 34.10-2001 but as of January 2016 deprecated (https://mta.openssl.org/pipermail/openssl-commits/2016-January/003023.html )
 
-    \subsubsection{Basic constraints}
+\subsection{Specification of validity}
+Validity is specified by CA at the moment of signing CSR.
 
-      \paragraph{Specify Type}
+\subsection{Basic Constraints}
+Specification of constraints is made by changing basicConstraints part in [ v3_req ] part of openssl.cnf of CA
+\begin{verbatim}
+[ v3_req ]
 
-      \paragraph{Specify path length}
+basicConstraints=critical,CA:BOOL_VAL,\
+ pathlen:<maxChainLengthInteger>
+\end{verbatim}
 
-  \subsection{Specifications}
+\subsection{Seting Subject Alternative Name for end certificates}
+To set SAN the change of subjectAltName in openssl.cnf is needed
+\begin{verbatim}
+[ v3_req ]
+subjectAltName = @alt_names
 
-    \subsubsection{Certificate Signing Request signing}
+[alt_names]
+DNS.1 = example1.com
+DNS.2 = example2.com
+DNS.<next_number> = dns_webaddress.com
+\end{verbatim}
 
-    \subsubsection{Create combination of private key and signed chain}
-
-    \subsubsection{Specify certificate validity}
-
-    \subsubsection{Setting Subject Alternative Name for end certificates}
-
-    \subsubsection{Support for Cryptographic Service Provider}
+\subsection{Using Cryptographic Service Provider}
+TO DO
 
 \section{Conversions}
+\subsection{PKCS12 and JKS conversion in OpenSSL}
 
-  \subsection{Exporting}
+\subsection{Export certificate only from PKCS12 file}
+It can be done with command:
+\begin{verbatim}
+openssl pkcs12 -in yourfile.pfx -clcerts \
+ -nokeys -out certificate.crt 
+\end{verbatim}
 
-    \subsubsection{Certificate or certificate chain from a file}
+\subsection{Export private key only from PKCS12 file}
+To export private key use command:
+\begin{verbatim}
+openssl pkcs12 -nocerts -in filename.pfx -out site.key
+\end{verbatim}
 
-    \subsubsection{Private key only}
+\subsection{Importing into PKCS12 file}
+should be possible with 
+\begin{verbatim}
+openssl pkcs12 -export -in file.pem -out file.p12 \
 
-  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-
-  \subsection{Importing certificates and keys into storage files}
+-name "My Certificate" -certfile \
+othercerts.pem but need to test it.
+\end{verbatim}
 

### 2016-08-27 TEX/draft.tex
Added text to git also changed back .tex file

--- 2016-08-24 TEX/draft.tex
@@
 \myparagraph{PEM encoded certificates (.pem$\vert$.cer$\vert$.crt):}
-
-  \verb+openssl x509 -in sample_cert.extention -text -noout+
-
+  \begin{verbatim}
+  openssl x509 -in sample_cert.extention -text -noout
+  \end{verbatim}
 \myparagraph{DER encoded certificates (.der):}
-
-  \verb+openssl x509 -in certificate.der -inform der -text -noout+
-
+  \begin{verbatim}
+  openssl x509 -in certificate.der -inform der -text -noout
+  \end{verbatim}
 \myparagraph{Importing PEM or DER encoded keys or certificates into PKCS\#12 file:}
-
-  \verb+openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem+
-
+  \begin{verbatim}
+  openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
+  \end{verbatim}
 certfile option is used only if importing more certificates into a single PKCS\#12 file is wanted.
@@
       \paragraph{Self-signed certificate}
+      It is possible to generate private key and self signed certificate with 
+      \begin{verbatim}
+      openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
+      \end{verbatim}
 
       \paragraph{Certificate Signing Request}
+      It is possible to generate private key and CSR with
+      \begin{verbatim}
+      openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
+      \end{verbatim}
 
@@
       \paragraph{Specify algorithm}
+      Currently OpenSSL supports Public-key cryptography algorithms:
+      RSA, DSA, Diffie-Hellman key exchange, Elliptic Curve
+
+      In the past also support for GOST R 34.10-2001 but as of January 2016 deprecated (https://mta.openssl.org/pipermail/openssl-commits/2016-January/003023.html )
 

### 2016-08-28 TEX/draft.tex
More changes to OpenSSL part, keytool part not even included as of now

@@
 \usepackage{adjustbox,lipsum}
-\usepackage{alltt} %for code snippets
+\usepackage{csquotes}
 
@@
   \begin{verbatim}
-  openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
+  openssl pkcs12 -export -in file.pem \
+          -inkey privateKeyFile.key -out file.p12 \
+          -name "My Certificate" -certfile othercerts.pem
   \end{verbatim}
@@
   \subsection{License}
-OpenSSL is free to use commercialy, however creating CA is not advised
-a) OPENSSL O'REILY page 59 
-b) hinted in manual pages.
-
+OpenSSL is free to use commercialy, however creating CA is not advised in O'REILLY's Network Security with OpenSSL by J. Viega, M. Messier and P. Chandra on page 59,
+\begin{displayquote}
+Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.
+\end{displayquote}
+and also hinted in manual pages:
+\begin{displayquote}
 The ca command is quirky and at times downright unfriendly.
@@
 The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results. 
+\end{displayquote}
 
@@
       \begin{verbatim}
-      openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
+      openssl req -x509 -sha256 -nodes -days 365 \
+	      -newkey rsa:[length] -keyout privateKey.key \
+              -out certificate_name.crt
       \end{verbatim}
@@
       \begin{verbatim}
-      openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
+      openssl req -out CSR.csr -new -newkey rsa:[length] \
+              -nodes -keyout privateKey.key
       \end{verbatim}
@@
       \paragraph{Specify length}
+      Length is specified while generating key/certificate.
 
@@
 
+    Basic constraints are defined in CA's openssl.cnf \verb+[ v3_req ]+ part.
+    \begin{verbatim}
+[ v3_req ]
+
+basicConstraints=critical,CA:<BOOL_VAL>, pathlen:<maxChainLengthInteger>
+    \end{verbatim}
+
       \paragraph{Specify Type}
-
+To specify if generated certificate belongs to CA or is end certificate you choose \verb+<BOOL_VAL>+ true or false respectively.
       \paragraph{Specify path length}
-
+Specifying of path length is made by setting a \verb+<maxCheinLengthInteger>+ to desired value (e.g. if generated certificate should be used only for generating end certificates the value is 0)
   \subsection{Specifications}
@@
     \subsubsection{Certificate Signing Request signing}
+   SR signing can be done by CA created in openSSL by command
+\begin{verbatim}
+openssl ca -config ca/openssl.cnf \
+        -extensions server_cert -days <validity_time>  \
+	-notext -md [message digest alg] -in ca/csr/www.example.com.csr.pem \
+        -out ca/certs/www.example.com.cert.pem
+\end{verbatim}
 
     \subsubsection{Create combination of private key and signed chain}
+    First creation of the request is needed, after that request must be signed. To combine them together the creation of PKCS\#12 file is needed with commands:
+\begin{verbatim}
+	openssl pkcs12 -export -out outfilename.p12 \
+	        -in signed_certificate.crt -inkey privateKey.key \
+	        -chain -CAfile ca-all.crt -password pass:PASSWORD
+\end{verbatim}
+    \subsubsection{Specify certificate validity}
+    Time how long the certificate will be valid can be given in csr but only as a suggestion. Ultimately the real time of validity is always given by CA signing the CSR.
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+    The Subject Alternative Name is also given in \verb+[ v3_req ]+ part of openssl.cnf that CA uses. It can be given as an IP address but also as a DNS name.
 
-    \subsubsection{Specify certificate validity}
+\begin{verbatim}
+[ v3_req ]
+subjectAltName = @alt_names
 
-    \subsubsection{Setting Subject Alternative Name for end certificates}
+[alt_names]
+DNS.1 = example1.com
+DNS.2 = example2.com
+DNS.<next_number> = dns_webaddress.com
+\end{verbatim}
 

### 2016-08-29 TEX/draft.tex
Finished OpenSSL text, need to abstract some more commands - unimportant - next step is to rewrite keytool part

@@
     \subsubsection{Support for Cryptographic Service Provider}
+OpenSSL has native support for Cryptographic Service Provider since version 0.9.7 by creating PKCS\#12 file using -CSP option to set the cspname parameter
+
+%Not totally sure of this http://www.drh-consultancy.demon.co.uk/pkcs12faq.html is my refference
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+    To export certificate from a PKCS\#12 file use:
+\begin{verbatim}
+openssl pkcs12 -in name.[pfx|p12] -nokeys -clcerts -out name.pem
+\end{verbatim}
+
+    To export certificate chain from a PKCS\#12 file use:
+\begin{verbatim}
+openssl pkcs12 -in name.[pfx|p12] -nokeys -cacerts -out CAchain.pem
+\end{verbatim}
+    It should be mentioned that if there are multiple certificates in a chain they are all going to be in same output file.
+
+    \subsubsection{Private key only}
+    To export an encrypted private key use:
+\begin{verbatim}
+openssl pkcs12 -in name.[pfx|p12] -nocerts -out name.encrypted.priv.key
+\end{verbatim}
+
+    To export an unencrypted private key use:
+\begin{verbatim}
+openssl pkcs12 -in name.[pfx|p12] -nocerts -nodes -out name.unencrypted.priv.key
+\end{verbatim}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+Direct conversion between Java Keystore and PKCS\#12 type file is not supported by OpenSSL 
+  \subsection{Importing certificates and keys into storage files}
+To import certificate and private key into a single PKCS\#12 type file use:
+\begin{verbatim}
+ openssl pkcs12 -export -out certificate.pfx \
+         -inkey privateKey.key -in certificate.crt \
+         -certfile CACert.crt
+\end{verbatim}
+
+\chapter{Keygen}
+
+\section{General}
+
+  \subsection{Type}
+
+  \subsection{View and information}
+
+  \subsection{License}
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+
+      \paragraph{Certificate Signing Request}
+
+      \paragraph{Specify length}
+
+      \paragraph{Specify algorithm}
+
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+
+      \paragraph{Specify path length}
+
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+
+    \subsubsection{Support for Cryptographic Service Provider}
 
@@
   \subsection{Importing certificates and keys into storage files}
-
-\chapter{Keygen}
 

### 2016-08-30 TEX/draft.tex
Started on Keytool Chapter

@@
   \subsection{Type}
+  Keytool has native support for both PKCS\#12 and Java KeyStore type files 
+  \subsection{View and information}
+  To view information about PEM or DER encoded certificate use:
+  \begin{verbatim}
+  keytool -printcert -file certificate.extention
+  \end{verbatim}
 
-  \subsection{View and information}
+  To view information about Jave KeyStore or PKCS\#12 encoded file use:
+  \begin{verbatim}
+  keytool -list -v -keystore store_file.[pfx|p12|jks]
+  \end{verbatim}
 
+  Viewing Public key part of certificate is not availiable in keytool.
   \subsection{License}

### 2016-08-31 TEX/draft.tex
Added more text to Keytool

@@
       \paragraph{Self-signed certificate}
+To generate new key pair and self-signed certificate use:
+\begin{verbatim}
+keytool -genkey -keyalg [RSA|DSA] -alias [alisaname] \
+        -keystore [keystore_file] -storepass [password] \
+        -validity [time] -keysize [length]
+\end{verbatim}
+
+Keytool natively supports only DSA of length in between 512 and 1024, and is considered to be dangerous to use. RSA with key length of at least 2048 is preffered.
 
       \paragraph{Certificate Signing Request}
-
+To generate a Certificate Signing Request generation of a key pair with alias is needed:
+\begin{verbatim}
+keytool -genkey -alias namealias -keyalg [RSA|DSA] \
+        –keysize [length] -keystore [keystore_path | new_keystore_name]
+\end{verbatim}
+To create a CSR you then need to do:
+\begin{verbatim}
+keytool -certreq -keyalg [keyalg_from_genkey] -alias [alias_from_genkey] -file certreq.csr -keystore [jks_from_genkey]
+\end{verbatim}
+Where you need to set -keyalg -alias and -keystore as chosen when generating key pair earlier.
       \paragraph{Specify length}
+Length is specified when generating keys, RSA support for up to 4096, DSA support from 512 up to 1024.
 
       \paragraph{Specify algorithm}
-
+Algorithm is specified while generating key pair, currently support for DSA, RSA. EC is needed to be implemented.      
     \subsubsection{Basic constraints}

### 2016-08-31 TEX/draft.tex
More text added

@@
       \paragraph{Specify Type}
-
+With keytool alone it is not possible to make CA certificate.
       \paragraph{Specify path length}
-
+Specifying of path length is not availiable.
   \subsection{Specifications}
@@
     \subsubsection{Certificate Signing Request signing}
-
+Keytool cannot be used to sign Certificate Signing Request.
     \subsubsection{Create combination of private key and signed chain}
@@
     \subsubsection{Specify certificate validity}
-
+Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option.
     \subsubsection{Setting Subject Alternative Name for end certificates}
-
+To set a Subject Alternative Name for certificate use \verb+-ext san=dns:www.dnsexample.com,ip:1.1.1.1+ which will add SAN to certificate   
     \subsubsection{Support for Cryptographic Service Provider}
@@
     \subsubsection{Private key only}
-
+Exporting of private key only is not availiable in keytool.
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}

### 2016-08-31 TEX/draft.tex
Almost finished text of keytool, want to look more into some parts

@@
   \subsection{License}
+%need to ask some things
 
@@
 keytool -genkey -alias namealias -keyalg [RSA|DSA] \
-        –keysize [length] -keystore [keystore_path | new_keystore_name]
+        -keysize [length] -keystore [keystore_path | new_keystore_name]
 \end{verbatim}
@@
 Where you need to set -keyalg -alias and -keystore as chosen when generating key pair earlier.
+
       \paragraph{Specify length}
@@
 With keytool alone it is not possible to make CA certificate.
+
       \paragraph{Specify path length}
 Specifying of path length is not availiable.
+
   \subsection{Specifications}
@@
 Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option.
+
     \subsubsection{Setting Subject Alternative Name for end certificates}
-To set a Subject Alternative Name for certificate use \verb+-ext san=dns:www.dnsexample.com,ip:1.1.1.1+ which will add SAN to certificate   
+To set a Subject Alternative Name for certificate use \verb+-ext san=dns:www.dnsexample.com,ip:1.1.1.1+ option which will add SAN to certificate.
+
     \subsubsection{Support for Cryptographic Service Provider}
+%unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found
 
@@
     \subsubsection{Certificate or certificate chain from a file}
+To export certificate with alias \verb+myalias+ use:
+\begin{verbatim}
+keytool -export -alias myalias -file [output.crt] -keystore [source_keystore.jks]
+\end{verbatim}  
+Exported certificate will be DER encoded.
+
+Exporting of certificate chain from a Java KeyStore is not availiable using keytool.
 
@@
 Exporting of private key only is not availiable in keytool.
+
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+Conversion between Java KeyStore and PKCS\#12 file is availiable. To convert Java KeyStore file to PKCS\#12 use:
+\begin{verbatim}
+keytool -importkeystore -srckeystore [existing_keystore.jks] \
+        -destkeystore [destination_filename.p12|pfx] -srcstoretype JKS \
+        -deststoretype PKCS12 -srcstorepass [.jks password] \
+        -deststorepass [same as .jks password] -srcalias [source_alias] \
+        -destalias [source_alias] -srckeypass [source_key_password] \
+        -destkeypass [source_key_password] -noprompt
+\end{verbatim}
+
+To convert PKCS\#12 to JKS use:
+\begin{verbatim}
+keytool -importkeystore -srckeystore [PKCS12_file.pfx|.p12] \
+        -srcstoretype pkcs12 -destkeystore [dest_keystore_name.jks] \
+        -deststoretype JKS
+\end{verbatim}
 

### 2016-09-06 TEX/draft.tex
Finalised a keytool part

@@
 OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
-Keygen                  & JKS    &                             &         \\ \hline
+Keygen                  & JKS    & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
 \end{tabular}
@@
 \begin{verbatim}
-keytool -certreq -keyalg [keyalg_from_genkey] -alias [alias_from_genkey] -file certreq.csr -keystore [jks_from_genkey]
+keytool -certreq -keyalg [keyalg_from_genkey] -alias [alias_from_genkey] \
+        -file certreq.csr -keystore [jks_from_genkey]
 \end{verbatim}
@@
       \paragraph{Specify Type}
-With keytool alone it is not possible to make CA certificate.
+With keytool you can make a self-signed CA certificate by using \verb+-ext ca:true+ option.
 
       \paragraph{Specify path length}
-Specifying of path length is not availiable.
+Specifying of path length is possible while making a certificate by using  \\
+\verb+-ext pathlen:[int path length]+ option.
 
@@
     \subsubsection{Certificate Signing Request signing}
-Keytool cannot be used to sign Certificate Signing Request.
+Keytool cannot be used to sign Certificate Signing Request. It can import certificate signed by CA but as a standalone tool cannot sign a CSR with a CA cert.
+%I'm sorry but i haven't found a way to sign a CSR with CA cert with keytool alone
+
     \subsubsection{Create combination of private key and signed chain}
-
+You can import a key pair into a Java KeyStore file along with signed chain if the signed chain is provided and a CA certificate is imported into said Java Keystore.
     \subsubsection{Specify certificate validity}
@@
     \subsubsection{Support for Cryptographic Service Provider}
+Support for Cryptographic service provider is native but there is need for a definition of path where the CSR is located.
+\begin{verbatim}
+-storetype [keystore_type_of_implementation]
+-provider [provider_implementation_name]
+-providerpath [provider_implementation_type]
+\end{verbatim}
 %unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found
@@
   \subsection{Importing certificates and keys into storage files}
+To import certificate use:
+\begin{verbatim}
+keytool -import -alias [certificate_chosen_alias] \
+        -file [certificate_file.ext] -keystore [target_keystore]  
+\end{verbatim}
+
+Importing of keys alone is not supported, you need to fold them into a Java KeyStore or PKCS\#12 file first.
 

### 2016-09-12 TEX/draft.tex
Almost final Keytool text, only need to write commands for signed chain, GnuPG will be added soon, just need to be sure about everything.

@@
 \begin{adjustbox}{max width=\textwidth}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
-\multirow{-2}{*}{Tools} & Type   & View and information        & License \\ \hline
-OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
-Keygen                  & JKS    & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
+                        & \multicolumn{4}{c|}{General}                                                             \\ \cline{2-5} 
+\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System \\ \hline
+OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & Both             \\ \hline
+Keygen                  & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & Both             \\ \hline
+GnuPG                   &        &                                                    &         &                  \\ \hline
+Keystore Explorer       &        &                                                    &         &                  \\ \hline
 \end{tabular}
@@
 
+\subsection{Operating Systems}
+In this part the Operating System where the tool is imported is defined.
+Both means that it is implemented under UNIX like systems and Windows systems.
+Otherwise the Operating System is defined (Windows | UNIX).
+
 \newpage
@@
 OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
-Keygen                 &                                                                      &                             &                             &                             &                             &                             \\ \hline
+Keytool                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
+Keystore explorer      &                                                                      &                             &                             &                             &                             &                             \\ \hline
 \end{tabular}
@@
 OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
-Keygen                 &                               &                                          &                                                &                                            &                                                                             \\ \hline
+Keygen                 & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
+GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
+Keystore explorer      &                               &                                          &                                                &                                            &                                                                             \\ \hline
 \end{tabular}
@@
 \hline
+                        & \multicolumn{4}{c|}{Conversions}                                                                                                                                            \\ \cline{2-5}
                         & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
-\multirow{-2}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
+\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
 OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
-Keygen                  &                                  &                             &                                         &                                                                  \\ \hline
-                        &                                  &                             &                                         &                                                                  \\ \hline
+Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
+Keystore explorer       &                                  &                             &                                         &                                                                  \\ \hline
 \end{tabular}
@@
 
-\chapter{Keygen}
+\chapter{Keytool}
 
@@
   \subsection{License}
-%need to ask some things
+Keytool is free to use in production code and is licensed under Apache Licence Version 2.0. For more detailed description look at http://www.apache.org/licenses/LICENSE-2.0.txt
 
@@
       \paragraph{Specify Type}
-With keytool you can make a self-signed CA certificate by using \verb+-ext ca:true+ option.
+With keytool you can make a self-signed CA certificate by using \verb+-ext BC=ca:[true|false]+ option.
 
@@
 Specifying of path length is possible while making a certificate by using  \\
-\verb+-ext pathlen:[int path length]+ option.
+\verb+-ext BC=pathlen:[int path length]+ option.
 
@@
     \subsubsection{Certificate Signing Request signing}
-Keytool cannot be used to sign Certificate Signing Request. It can import certificate signed by CA but as a standalone tool cannot sign a CSR with a CA cert.
-%I'm sorry but i haven't found a way to sign a CSR with CA cert with keytool alone
+Keytool can sign a CSR if a CA certificate and a keystore containing it are avaliable:
+\begin{verbatim}
+keytool -gencert -rfc -keystore [root_keystore.jks] \
+        -alias [CA_cert_alias] -storepass [store_password] \
+        -infile [CSR_file.csr] -validity <int_length> \
+        -outfile [output_certificate.crt] -ext BC=ca:[true|false] \
+        -ext SAN=ip:<IP_address>,dn:<DNS_address> 
+\end{verbatim}
 
@@
     \subsubsection{Support for Cryptographic Service Provider}
-Support for Cryptographic service provider is native but there is need for a definition of path where the CSR is located.
+Support for Cryptographic Service Provider is native but there is need for a definition of path where the CSP is located.
 \begin{verbatim}
@@
 Importing of keys alone is not supported, you need to fold them into a Java KeyStore or PKCS\#12 file first.
+
+\chapter{GnuPG}
+
+\section{General}
+
+  \subsection{Type}
+
+  \subsection{View and information}
+
+  \subsection{License}
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+
+      \paragraph{Certificate Signing Request}
+
+      \paragraph{Specify length}
+
+      \paragraph{Specify algorithm}
+
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+
+      \paragraph{Specify path length}
+
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+
+    \subsubsection{Support for Cryptographic Service Provider}
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+
+    \subsubsection{Private key only}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+
+  \subsection{Importing certificates and keys into storage files}
+
+\chapter{Keystore Explorer}
+
+\section{General}
+
+  \subsection{Type}
+
+  \subsection{View and information}
+
+  \subsection{License}
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+
+      \paragraph{Certificate Signing Request}
+
+      \paragraph{Specify length}
+
+      \paragraph{Specify algorithm}
+
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+
+      \paragraph{Specify path length}
+
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+
+    \subsubsection{Support for Cryptographic Service Provider}
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+
+    \subsubsection{Private key only}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+
+  \subsection{Importing certificates and keys into storage files}
 

### 2016-09-20 TEX/draft.tex
Started writing text, will finish tonight, also will add screenshots.

@@
   \subsection{Type}
-
+The type of file with which GnuPG works is a .gpg encoded in OpenPGP standard. As I understood the OpenPGP is competing standard to X509 standard.  
   \subsection{View and information}
@@
   \subsection{License}
+GnuPG is free to use both for testing and in production code.
 
@@
       \paragraph{Self-signed certificate}
-
+Generation of keys and self-signed certificate is not supported. In older versions it was possigle with \verb+gpgm+
       \paragraph{Certificate Signing Request}
@@
 
+%KEYSTORE EXPLORER PART 
 \chapter{Keystore Explorer}
@@
   \subsection{Type}
-
+Keystore Explorer supports both Java Keystore and PKCS\#12 type files, in addition it has a support for alternatives to JKS such as JCEKS, BKS, BKS-V1, UBER.
   \subsection{View and information}
-
+You can view certificates and additional information with Keystore Explorer, view public and private key parts of certificates and other info such as subject alternative names.
   \subsection{License}
+Keystore Explorer is free to use utility, License is public.
 
@@
       \paragraph{Self-signed certificate}
-
+It is possible to generate a key pair and self-signed certificate, simply clic on icon or double clic on blank space, choose algorithm and key length.
+Then you can choose all the other options such as Basic Constraints and Subject Alternative Name.
+%place for screenshots, will do from Windows.
+You can also set up deaful pre-fill of Common Name, Organisational Unit, Organisation etc.
+%pictures of setting
       \paragraph{Certificate Signing Request}

### 2016-09-20 TEX/draft.tex
Added text to keystore, will add screenshots tommorow.

@@
       \paragraph{Certificate Signing Request}
-
+It is possible to make Certificate Signing Request in Keystore Explorer. Simply generate keys and then do not change Basic Constraints v3 part of certificate.      
       \paragraph{Specify length}
-
+Length can be specifyied when making key but ultimately it is confirmed by Certificate Authority when signing a CSR.
       \paragraph{Specify algorithm}
-
+Algorithm is specified when generating keys and also confirmed by certificate authority.
     \subsubsection{Basic constraints}
@@
       \paragraph{Specify Type}
-
+Specifying type is made while generating keys and certificate by changing v3 portion when asked during generation.
       \paragraph{Specify path length}
-
+Specifying of path length is made also by changing v3 part of x509 certificate during generation under Basic Constraints type.
   \subsection{Specifications}
@@
     \subsubsection{Certificate Signing Request signing}
-
+To sign a Certificate Signing Request simply right-click a Certificate Authority certificate and use the sign with option.
     \subsubsection{Create combination of private key and signed chain}
@@
     \subsubsection{Specify certificate validity}
-
+Desired duration of certificate validity is asked during generation, but given whilst signing a Certificate Signing Request by Certificate Authority
     \subsubsection{Setting Subject Alternative Name for end certificates}
-
+Setting of Subject Alternative Name for certificate is made during generation of CSR, under the v3 part of certificate under the Basic Constraints type.
     \subsubsection{Support for Cryptographic Service Provider}
-
+As Far as i know there is not support for using CSP.
 \section{Conversions}
@@
     \subsubsection{Certificate or certificate chain from a file}
-
+It is possible to export a certificate from a keystore type by simply right-clicking the chosen certificate and chosing export option.
     \subsubsection{Private key only}
-
+It is possible to export a private key from a keystore type by simply right-clicking the chosen certificate and chosing export->private key option.
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
@@
   \subsection{Importing certificates and keys into storage files}
+ It is possible to import a certificate and/or key by chosing Import option.
 

### 2016-09-21 TEX/draft.tex
Added screenshots, cant format them properly yet, will do tommorow/the day after. Also added Screenshot files under Dependancies directory. Also finally finished overview tables for tested tools.

--- 2016-09-20 TEX/draft.tex
@@
 \usepackage{csquotes}
-
+\usepackage{graphicx}
 \newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\} %used for better formating of some text
@@
 \multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System                   \\ \hline
-OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & Both             \\ \hline
-Keygen                  & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & Both             \\ \hline
+OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
+Keytool                 & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
 GnuPG                   &        &                                                    &         &                                    \\ \hline
-Keystore Explorer       &        &                                                    &         &                  \\ \hline
+Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
 \end{tabular}
@@
 GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
-Keystore explorer      &                                                                      &                             &                             &                             &                             &                             \\ \hline
+Keystore explorer      & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 \end{tabular}
@@
 OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
-Keygen                 & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
+Keytool                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
 GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
-Keystore explorer      &                               &                                          &                                                &                                            &                                                                             \\ \hline
+Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
 \end{tabular}
@@
 GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
-Keystore explorer       &                                  &                             &                                         &                                                                  \\ \hline
+Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
 \end{tabular}
@@
 Keystore Explorer supports both Java Keystore and PKCS\#12 type files, in addition it has a support for alternatives to JKS such as JCEKS, BKS, BKS-V1, UBER.
+
+\includegraphics{../Dependancies/Keystore_Explorer/Type.jpg}
   \subsection{View and information}
-You can view certificates and additional information with Keystore Explorer, view public and private key parts of certificates and other info such as subject alternative names.
+You can view certificates and additional information with Keystore Explorer, view public and private key parts of certificates and other info such as subject alternative names by right clicking a certificate and choosing viable option from View option.
   \subsection{License}
@@
       \paragraph{Self-signed certificate}
-It is possible to generate a key pair and self-signed certificate, simply clic on icon or double clic on blank space, choose algorithm and key length.
+It is possible to generate a key pair and self-signed certificate, simply click on icon or double click on blank space, choose algorithm and key length.
 Then you can choose all the other options such as Basic Constraints and Subject Alternative Name.
-%place for screenshots, will do from Windows.
-You can also set up deaful pre-fill of Common Name, Organisational Unit, Organisation etc.
-%pictures of setting
+
+\includegraphics{../Dependancies/Keystore_Explorer/genKeys.jpg}
+\includegraphics{../Dependancies/Keystore_Explorer/genCert.jpg}
+You can also set up default pre-fill of Common Name, Organisational Unit, Organisation etc.
+
       \paragraph{Certificate Signing Request}
-
+It is possible to make Certificate Signing Request in Keystore Explorer. Simply generate key pair certificate and then right click the generated certificate and choose Generate CSR option.
+\includegraphics{../Dependancies/Keystore_Explorer/genCSR.jpg}
       \paragraph{Specify length}
-
+Length is specified at the moment of key pair generation.
       \paragraph{Specify algorithm}
-
+Algorithm of keys is specified when generating keys and the certificate hash function is chosen by certificate authority.
     \subsubsection{Basic constraints}
 
+\includegraphics{../Dependancies/Keystore_Explorer/Basic_Constraints.jpg}
+
       \paragraph{Specify Type}
-
+Specifying type is made while generating keys and certificate by changing v3 portion when asked during generation.
       \paragraph{Specify path length}
-
+Specifying of max path length is made also by changing v3 part of x509 certificate during generation under Basic Constraints type.
   \subsection{Specifications}
@@
     \subsubsection{Certificate Signing Request signing}
+To sign a Certificate Signing Request simply right-click a Certificate Authority certificate and use the sign->CSR option.
+Then you need to import CA response that was generated in a desired place into a certificate from which the CSR was generated.
 
+\includegraphics{../Dependancies/Keystore_Explorer/CSRsign.jpg}
     \subsubsection{Create combination of private key and signed chain}
+To create combination of private key simply generate new key pair certificate, export private key part, import it back and then import to new certificate of private key a trusted chain.
 
     \subsubsection{Specify certificate validity}
-
+Desired duration of certificate validity is asked during generation, but given whilst signing a Certificate Signing Request by Certificate Authority
     \subsubsection{Setting Subject Alternative Name for end certificates}
-
+Setting of Subject Alternative Name for certificate is made during generation of certificate, under the add extentions option under the Subject Alternative Name part.
+Keystore Explorer allows to add both DNS and IP formats of SAN.
     \subsubsection{Support for Cryptographic Service Provider}
-
+As Far as i know there is not support for using CSP.
 \section{Conversions}
@@
     \subsubsection{Certificate or certificate chain from a file}
-
+It is possible to export a certificate or certificate chain from a keystore by simply right-clicking the chosen certificate and chosing export option.
     \subsubsection{Private key only}
+It is possible to export a private key from a keystore by simply right-clicking the chosen certificate and chosing export->private key option.
 
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+To change a type of file simply right-click on the blank space and choose change type option.
+In addition to changing a pkcs12 file type to JKS it is possible to change type of files between all supported types of Keystore Explorer.
 
   \subsection{Importing certificates and keys into storage files}
+It is possible to import a certificate and/or key by chosing Import option.
 

### 2016-09-28 TEX/draft.tex
Due to an illness not much of a work has been done, screenshots of Keystore Explorer were finally formated, text and tables about XCA added, need to finalize some parts of text and add screenshots.

@@
 Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
+XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
 \end{tabular}
@@
 Keystore explorer      & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+XCA                    & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 \end{tabular}
@@
 Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
+XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & ???
+\\ \hline
 \end{tabular}
@@
 Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
 \end{tabular}
@@
 Said keys/certificates can then be stored inside single .pfx file.
-
+  \cellcolor[HTML]{34FF34}Yes             
   \subsection{View and information}
@@
       \end{verbatim}
-
+      \cellcolor[HTML]{34FF34}Yes             
       \paragraph{Certificate Signing Request}
@@
 Keystore Explorer supports both Java Keystore and PKCS\#12 type files, in addition it has a support for alternatives to JKS such as JCEKS, BKS, BKS-V1, UBER.
-
-\includegraphics{../Dependancies/Keystore_Explorer/Type.jpg}
+\begin{figure}[!ht]
+ \caption{Choosing type}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/Keystore_Explorer/Type.jpg}
+\end{figure}
   \subsection{View and information}
@@
 Then you can choose all the other options such as Basic Constraints and Subject Alternative Name.
+\begin{figure}[!ht]
+ \caption{Generating keys}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/Keystore_Explorer/genKeys.jpg}
+\end{figure}
 
-\includegraphics{../Dependancies/Keystore_Explorer/genKeys.jpg}
-\includegraphics{../Dependancies/Keystore_Explorer/genCert.jpg}
+\begin{figure}[!ht]
+ \caption{Generating certificate}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/Keystore_Explorer/genCert.jpg}
+\end{figure}
+
 You can also set up default pre-fill of Common Name, Organisational Unit, Organisation etc.
@@
 It is possible to make Certificate Signing Request in Keystore Explorer. Simply generate key pair certificate and then right click the generated certificate and choose Generate CSR option.
-\includegraphics{../Dependancies/Keystore_Explorer/genCSR.jpg}
+\begin{figure}[!ht]
+ \caption{Generating a CSR}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/Keystore_Explorer/genCSR.jpg}
+\end{figure}
+
       \paragraph{Specify length}
@@
     \subsubsection{Basic constraints}
-
-\includegraphics{../Dependancies/Keystore_Explorer/Basic_Constraints.jpg}
+\begin{figure}[!ht]
+ \caption{Basic Constraints}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/Keystore_Explorer/Basic_Constraints.jpg}
+\end{figure}
 
@@
 
-\includegraphics{../Dependancies/Keystore_Explorer/CSRsign.jpg}
+\begin{figure}[!ht]
+ \caption{Signing of a CSR}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/Keystore_Explorer/CSRsign.jpg}
+\end{figure}
+
     \subsubsection{Create combination of private key and signed chain}
@@
 It is possible to import a certificate and/or key by chosing Import option.
+
+\chapter{XCA}
+
+\section{General}
+
+  \subsection{Type}
+XCA works with PKCS\#12 type files, but it is neccessary to make theirs database file which stores and to which you can import certificates, certificate signing requests or keys.
+  \subsection{View and information}
+You can view information about keys, certificates and CSRs by double clicking a chosen file.
+  \subsection{License}
+XCA is under BSD License - it is free to use for testing and also commercialy.
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+You can generate key pair by itself and then use it for generation of certificate.
+If you do not generate key in advance there is option to generate new key whilst generating a certificate.
+To generate a certificate click on Certificates tab and press New Certificate.
+There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm (\verb+MD5|SHA1|SHA224|SHA256|SHA384|SHA512|RIPEMD160+).
+Under Subject tab, you shoose Common Name, Organisation, etc.
+fields of certificate and also choose private key.
+If you didn't generate key in advance then you can generate a new private key (\verb+RSA|DSA|EC+).
+For certificate to be accepted by all operating systems you need to choose \verb+Digital Signature & Key Agreement & Certificate Sign+ under Key usage tab.
+%WILL ADD SCREENSHOTS LATER
+      \paragraph{Certificate Signing Request}
+Certificate Signing Request is generated simmilarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
+      \paragraph{Specify length}
+Length of keys is specified during generation of keys.
+      \paragraph{Specify algorithm}
+Algorithm used for key generation is specified during generation of keys (\verb+RSA|DSA|EC+).
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+Type of a certificate is chosen under Extensions tab.
+      \paragraph{Specify path length}
+Path Length is also specified under Extensions tab.
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+Time period during which is a certificate valid is defined under Extensions tab.
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+Subject Alternative Names are specified in appropriate section under a Extensions tab.
+    \subsubsection{Support for Cryptographic Service Provider}
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+
+    \subsubsection{Private key only}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+
+  \subsection{Importing certificates and keys into storage files}
 

### 2016-10-05 TEX/draft.tex
XCA text and dependancies moving to notebook to commit final text, add screenshots and also GnuTLS text.

@@
     \subsubsection{Certificate Signing Request signing}
-
+To sign CSR you must have a CA certificate already in XCA's database.
+If a CA is availiable then you can sign CSR by using New Certificate option under Certificates tab or right click on CSR under Certificate signing requests tab and choose Sign option.
+Both options are equivalent.
     \subsubsection{Create combination of private key and signed chain}
-
+If the private key is provided PEM encoded it can be imported to XCA's database.
+If not you need to generate new key pair, then use export option to export private part of a key, delete key pair from database and then import private key.
+to create a combination, simply generate new certificate while using said private key.
     \subsubsection{Specify certificate validity}
@@
     \subsubsection{Support for Cryptographic Service Provider}
-
+As far as i know there is no support for CSP.
 \section{Conversions}
@@
     \subsubsection{Certificate or certificate chain from a file}
-
+Possible by using export option, choosing in which format you want to export it.
     \subsubsection{Private key only}
-
+Exporting of private key only directly is not availiable.
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-
+Conversion between PKCS\#12 and JKS is not possible.
   \subsection{Importing certificates and keys into storage files}

### 2016-10-06 TEX/draft.tex
Need to get some sleep

@@
 XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
+GnuTLS                  & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX       \\ \hline
 \end{tabular}
@@
 There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm (\verb+MD5|SHA1|SHA224|SHA256|SHA384|SHA512|RIPEMD160+).
+What must be changed is default hash function because it is set to SHA-1 which is no longer considered safe.
 Under Subject tab, you shoose Common Name, Organisation, etc.
@@
 For certificate to be accepted by all operating systems you need to choose \verb+Digital Signature & Key Agreement & Certificate Sign+ under Key usage tab.
-%WILL ADD SCREENSHOTS LATER
+\begin{figure}[!ht]
+ \caption{Generation of key for new cert}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/genKey.jpg}
+\end{figure}
+
+\begin{figure}[!ht]
+ \caption{Specify use}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/genKey_specif.jpg}
+\end{figure}
+
       \paragraph{Certificate Signing Request}
 Certificate Signing Request is generated simmilarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
+\begin{figure}[!ht]
+ \caption{Generation of CSR}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/newCSR.jpg}
+\end{figure}
+
       \paragraph{Specify length}
@@
 Algorithm used for key generation is specified during generation of keys (\verb+RSA|DSA|EC+).
+\begin{figure}[!ht]
+ \caption{Specifying of length and algorithm used}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/genKeylength.jpg}
+\end{figure}
+
     \subsubsection{Basic constraints}
@@
 Path Length is also specified under Extensions tab.
+
+\begin{figure}[!ht]
+ \caption{Basic constraints, validity and SAN}
+ \centering
+  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/BC_ext.png}
+\end{figure}
+
   \subsection{Specifications}
@@
 Conversion between PKCS\#12 and JKS is not possible.
+  \subsection{Importing certificates and keys into storage files}
+Certificates and keys can be Exported and imported to/from PKCS or PEM type files.
+
+\chapter{GnuTLS}
+
+\section{General}
+
+  \subsection{Type}
+GnuTLS works with PKCS\#12 PEM encoded files
+  \subsection{View and information}
+To view information about certificate use \verb+certtool --certificate-info --infile [file.pem]+ option.
+  \subsection{License}
+GnuTLS is under Gnu Public License \- free to use commercialy.
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+
+      \paragraph{Certificate Signing Request}
+
+      \paragraph{Specify length}
+
+      \paragraph{Specify algorithm}
+
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+
+      \paragraph{Specify path length}
+
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+
+    \subsubsection{Create combination of private key and signed chain}
+
+    \subsubsection{Specify certificate validity}
+
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+
+    \subsubsection{Support for Cryptographic Service Provider}
+
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+
+    \subsubsection{Private key only}
+
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+
   \subsection{Importing certificates and keys into storage files}

### 2016-10-13 TEX/draft.tex
Added GnuTLS, some parts little bit rough

@@
 XCA                    & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+GnuTLS                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 \end{tabular}
@@
 \\ \hline
+GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & ???	                                  & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
 \end{tabular}
@@
 XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FF3A3A}No  & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
 \end{tabular}
@@
       \paragraph{Self-signed certificate}
+To generate a self-signed certificate it is needed to generate a a private key. Generating of key is done by following command:
+\begin{verbatim}
+ certtool --generate-privkey --outfile [file.pem] --[rsa|dsa|ecc] \
+          --sec-param=[low|legacy|medium|high|ultra]
+\end{verbatim}
+Where \verb+sec-param=<length_alias>+ and will be discussed in next parts.
+
+To create a self-signed certificate with created private key use:
+\begin{verbatim}
+certtool --generate-self-signed --load-privkey ca-key.pem \
+         [--template cert.cfg] --hash=[look@algorithm_part] --outfile ca-cert.pem
+\end{verbatim}
+
+More options when generating self-signed certificate (or a CSR) you need to create a config file which has structure as follows (copied from a man page):
+\begin{verbatim}
+# X.509 Certificate options
+#
+# DN options
+
+# The organization of the subject.
+organization = "Koko inc."
+
+# The organizational unit of the subject.
+unit = "sleeping dept."
+
+# The locality of the subject.
+# locality =
+
+# The state of the certificate owner.
+state = "Attiki"
+
+# The country of the subject. Two letter code.
+country = GR
+
+# The common name of the certificate owner.
+cn = "Cindy Lauper"
+
+# A user id of the certificate owner.
+#uid = "clauper"
+
+# Set domain components
+#dc = "name"
+#dc = "domain"
+
+# If the supported DN OIDs are not adequate you can set
+# any OID here.
+# For example set the X.520 Title and the X.520 Pseudonym
+# by using OID and string pairs.
+#dn_oid = "2.5.4.12 Dr."
+#dn_oid = "2.5.4.65 jackal"
+
+# This is deprecated and should not be used in new
+# certificates.
+# pkcs9_email = "none@none.org"
+
+# An alternative way to set the certificate's distinguished name directly
+# is with the "dn" option. The attribute names allowed are:
+# C (country), street, O (organization), OU (unit), title, CN (common name),
+# L (locality), ST (state), placeOfBirth, gender, countryOfCitizenship, 
+# countryOfResidence, serialNumber, telephoneNumber, surName, initials, 
+# generationQualifier, givenName, pseudonym, dnQualifier, postalCode, name, 
+# businessCategory, DC, UID, jurisdictionOfIncorporationLocalityName, 
+# jurisdictionOfIncorporationStateOrProvinceName,
+# jurisdictionOfIncorporationCountryName, XmppAddr, and numeric OIDs.
+
+#dn = "cn = Nikos,st = New\, Something,C=GR,surName=Mavrogiannopoulos,2.5.4.9=Arkadias"
+
+# The serial number of the certificate
+# Comment the field for a time-based serial number.
+serial = 007
+
+# In how many days, counting from today, this certificate will expire.
+# Use -1 if there is no expiration date.
+expiration_days = 700
+
+# Alternatively you may set concrete dates and time. The GNU date string 
+# formats are accepted. See:
+# http://www.gnu.org/software/tar/manual/html_node/Date-input-formats.html
+
+#activation_date = "2004-02-29 16:21:42"
+#expiration_date = "2025-02-29 16:24:41"
+
+# X.509 v3 extensions
+
+# A dnsname in case of a WWW server.
+#dns_name = "www.none.org"
+#dns_name = "www.morethanone.org"
+
+# An othername defined by an OID and a hex encoded string
+#other_name = "1.3.6.1.5.2.2 302ca00d1b0b56414e5245494e2e4f5247a11b3019a006020400000002a10f300d1b047269636b1b0561646d696e"
+#other_name_utf8 = "1.2.4.5.6 A UTF8 string"
+#other_name_octet = "1.2.4.5.6 A string that will be encoded as ASN.1 octet string"
+
+# Allows writing an XmppAddr Identifier
+#xmpp_name = juliet@im.example.com
+
+# Names used in PKINIT
+#krb5_principal = user@REALM.COM
+#krb5_principal = HTTP/user@REALM.COM
+
+# A subject alternative name URI
+#uri = "http://www.example.com"
+
+# An IP address in case of a server.
+#ip_address = "192.168.1.1"
+
+# An email in case of a person
+email = "none@none.org"
+
+# TLS feature (rfc7633) extension. That can is used to indicate mandatory TLS
+# extension features to be provided by the server. In practice this is used
+# to require the Status Request (extid: 5) extension from the server. That is,
+# to require the server holding this certificate to provide a stapled OCSP response.
+# You can have multiple lines for multiple TLS features.
+
+# To ask for OCSP status request use:
+#tls_feature = 5
+
+# Challenge password used in certificate requests
+challenge_password = 123456
+
+# Password when encrypting a private key
+#password = secret
+
+# An URL that has CRLs (certificate revocation lists)
+# available. Needed in CA certificates.
+#crl_dist_points = "http://www.getcrl.crl/getcrl/"
+
+# Whether this is a CA certificate or not
+#ca
+
+# Subject Unique ID (in hex)
+#subject_unique_id = 00153224
+
+# Issuer Unique ID (in hex)
+#issuer_unique_id = 00153225
+
+#### Key usage
+
+# The following key usage flags are used by CAs and end certificates
+
+# Whether this certificate will be used to sign data (needed
+# in TLS DHE ciphersuites). This is the digitalSignature flag
+# in RFC5280 terminology.
+signing_key
+
+# Whether this certificate will be used to encrypt data (needed
+# in TLS RSA ciphersuites). Note that it is preferred to use different
+# keys for encryption and signing. This is the keyEncipherment flag
+# in RFC5280 terminology.
+encryption_key
+
+# Whether this key will be used to sign other certificates. The
+# keyCertSign flag in RFC5280 terminology.
+#cert_signing_key
+
+# Whether this key will be used to sign CRLs. The
+# cRLSign flag in RFC5280 terminology.
+#crl_signing_key
+
+# The keyAgreement flag of RFC5280. It's purpose is loosely
+# defined. Not use it unless required by a protocol.
+#key_agreement
+
+# The dataEncipherment flag of RFC5280. It's purpose is loosely
+# defined. Not use it unless required by a protocol.
+#data_encipherment
+
+# The nonRepudiation flag of RFC5280. It's purpose is loosely
+# defined. Not use it unless required by a protocol.
+#non_repudiation
+
+#### Extended key usage (key purposes)
+
+# The following extensions are used in an end certificate
+# to clarify its purpose. Some CAs also use it to indicate
+# the types of certificates they are purposed to sign.
+
+# Whether this certificate will be used for a TLS client;
+# this sets the id-kp-serverAuth (1.3.6.1.5.5.7.3.1) of 
+# extended key usage.
+#tls_www_client
+
+# Whether this certificate will be used for a TLS server;
+# This sets the id-kp-clientAuth (1.3.6.1.5.5.7.3.2) of 
+# extended key usage.
+#tls_www_server
+
+# Whether this key will be used to sign code. This sets the
+# id-kp-codeSigning (1.3.6.1.5.5.7.3.3) of extended key usage
+# extension.
+#code_signing_key
+
+# Whether this key will be used to sign OCSP data. This sets the
+# id-kp-OCSPSigning (1.3.6.1.5.5.7.3.9) of extended key usage extension.
+#ocsp_signing_key
+
+# Whether this key will be used for time stamping. This sets the
+# id-kp-timeStamping (1.3.6.1.5.5.7.3.8) of extended key usage extension.
+#time_stamping_key
+
+# Whether this key will be used for email protection. This sets the
+# id-kp-emailProtection (1.3.6.1.5.5.7.3.4) of extended key usage extension.
+#email_protection_key
+
+# Whether this key will be used for IPsec IKE operations (1.3.6.1.5.5.7.3.17).
+#ipsec_ike_key
+
+## adding custom key purpose OIDs
+
+# for microsoft smart card logon
+# key_purpose_oid = 1.3.6.1.4.1.311.20.2.2
+
+# for email protection
+# key_purpose_oid = 1.3.6.1.5.5.7.3.4
+
+# for any purpose (must not be used in intermediate CA certificates)
+# key_purpose_oid = 2.5.29.37.0
+
+### end of key purpose OIDs
+
+### Adding arbitrary extensions
+# This requires to provide the extension OIDs, as well as the extension data in
+# hex format. The following two options are available since GnuTLS 3.5.3.
+#add_extension = "1.2.3.4 0x0AAB01ACFE"
+
+# As above but encode the data as an octet string
+#add_extension = "1.2.3.4 octet_string(0x0AAB01ACFE)"
+
+# For portability critical extensions shouldn't be set to certificates.
+#add_critical_extension = "5.6.7.8 0x1AAB01ACFE"
+
+# When generating a certificate from a certificate
+# request, then honor the extensions stored in the request
+# and store them in the real certificate.
+#honor_crq_extensions
+
+# Alternatively only specific extensions can be copied.
+#honor_crq_ext = 2.5.29.17
+#honor_crq_ext = 2.5.29.15
+
+# Path length contraint. Sets the maximum number of
+# certificates that can be used to certify this certificate.
+# (i.e. the certificate chain length)
+#path_len = -1
+#path_len = 2
+
+# OCSP URI
+# ocsp_uri = http://my.ocsp.server/ocsp
+
+# CA issuers URI
+# ca_issuers_uri = http://my.ca.issuer
+
+# Certificate policies
+#policy1 = 1.3.6.1.4.1.5484.1.10.99.1.0
+#policy1_txt = "This is a long policy to summarize"
+#policy1_url = http://www.example.com/a-policy-to-read
+
+#policy2 = 1.3.6.1.4.1.5484.1.10.99.1.1
+#policy2_txt = "This is a short policy"
+#policy2_url = http://www.example.com/another-policy-to-read
+
+# Name constraints
+
+# DNS
+#nc_permit_dns = example.com
+#nc_exclude_dns = test.example.com
+
+# EMAIL
+#nc_permit_email = "nmav@ex.net"
+
+# Exclude subdomains of example.com
+#nc_exclude_email = .example.com
+
+# Exclude all e-mail addresses of example.com
+#nc_exclude_email = example.com
+
+# IP
+#nc_permit_ip = 192.168.0.0/16
+#nc_exclude_ip = 192.168.5.0/24
+#nc_permit_ip = fc0a:eef2:e7e7:a56e::/64
+
+# Options for proxy certificates
+#proxy_policy_language = 1.3.6.1.5.5.7.21.1
+
+# Options for generating a CRL
+
+# The number of days the next CRL update will be due.
+# next CRL update will be in 43 days
+#crl_next_update = 43
+
+# this is the 5th CRL by this CA
+# Comment the field for a time-based number.
+#crl_number = 5
+
+# Specify the update dates more precisely.
+#crl_this_update_date = "2004-02-29 16:21:42"
+#crl_next_update_date = "2025-02-29 16:24:41"
+
+# The date that the certificates will be made seen as
+# being revoked.
+#crl_revocation_date = "2025-02-29 16:24:41"
+\end{verbatim}
 
       \paragraph{Certificate Signing Request}
-
+Creating of CSR is made by:
+\begin{verbatim}
+certtool --generate-request --load-privkey [keyfile.pem] \
+         [--template cert.cfg]--outfile [csrfilename.pem]
+\end{verbatim}
+
+when not using template it uses default values 
+%need to find out what those are
       \paragraph{Specify length}
-
+Length is specified when generating keys by \verb+--sec-param=[low|legacy|medium|high|ultra]+ where length is determined by alias and algorithm.
+For RSA:
+\begin{verbatim}
+low    = 1024 bit
+legacy = 1776 bit
+medium = 2048 bit
+high   = 3072 bit
+ultra  = 15424 bit
+\end{verbatim}
+For DSA:
+\begin{verbatim}
+low    = 1024 bit
+legacy = 2048 bit
+medium = 2048 bit
+high   = 3072 bit
+ultra  = 3072 bit
+\end{verbatim}
+For ECDSA:
+\begin{verbatim}
+low    = 160 bit
+legacy = 192 bit
+medium = 224 bit
+high   = 256 bit
+ultra  = 512 bit
+\end{verbatim}
+
+to define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512+ option while generating a certificate.
       \paragraph{Specify algorithm}
+Algorithm for key generation is specified in \verb+--[rsa|dsa|ecc]+ option where rsa = RSA, dsa = DSA, ecc = ECDSA.
 
@@
       \paragraph{Specify Type}
-
+To specify whether certificate should be CA or End cert write \verb+ca+ into the cert.cfg file and use that as a template for generation. 
       \paragraph{Specify path length}
+Path length is specified by \verb+path_len=<value>+ option in cert.cfg file, where value is max chain length ( use -1 for undefined value).
 
@@
     \subsubsection{Certificate Signing Request signing}
-
+Possible %but i need to look wy it does not work for me
     \subsubsection{Create combination of private key and signed chain}
-
+When you create a certificate by signing a request to sign key only, you can validate chain. %but i think that is not what is regarded here as signed chain    
     \subsubsection{Specify certificate validity}
+Validity is specified by changing cert.cfg file used while generating a certificate, the part \verb+expiration_days = <value>+
+Alternatively, you cen set NOT BEFORE and NOT AFTER times by changing \verb+activation_date = <NOT_BEFORE_STRING>+ and \verb+expiration_date = <NOT_AFTER_STRING>+ where the times are written in GNU date string format.
 
     \subsubsection{Setting Subject Alternative Name for end certificates}
+SAN is set by adding options to cert.cfg :
+\begin{verbatim}
+dns_name = "www.dnsname1.com"
+dns_name = "www.dnsname2.com"
+  ...
+dns_name = "www.lastdns.com"
+
+uri = "uri1"
+...
+
+ip_address = "0.0.0.1"
+ip_address = "0.0.0.2"
+   ...
+\end{verbatim}
 
     \subsubsection{Support for Cryptographic Service Provider}
-
+GnuTLS does not have support for CSP.
 \section{Conversions}
@@
     \subsubsection{Private key only}
-
+It is not possible to export private key only, however for proper use of GnuTLS keys need to be stored on drive or imported to PKCS\#12 file.
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-
+Not possible.
   \subsection{Importing certificates and keys into storage files}
+Possible. - need to run up some facts.
 

### 2016-10-24 TEX/draft.tex
Added corrections

@@
     \subsubsection{Private key only}
-Exporting of private key only directly is not availiable.
+Exporting of private key only directly is availiable.
   \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
@@
 
-to define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512+ option while generating a certificate.
+Also, to choose exact bit length you can use \verb+--bits=<length>+ option - tested on \verb+--rsa --bits=32768+ option which generated 32kbit RSA key.
+
+To define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512+ option while generating a certificate.
+
       \paragraph{Specify algorithm}

### 2016-10-26 TEX/draft.tex
Added Makecert

@@
 GnuTLS                  & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX      \\ \hline
+Makecert                & PKCS12 & \cellcolor[HTML]{FE0000}No			      & Public  & \cellcolor[HTML]{FFC702}Windows    \\ \hline
 \end{tabular}
@@
 GnuTLS                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+Makecert               & \cellcolor[HTML]{34FF34}Yes					      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFFFFF}    & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 \end{tabular}
@@
 GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & ???	                                  & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
+Makecert	       & \cellcolor[HTML]{FE0000}No    &   \cellcolor[HTML]{FE0000}No	 	  & \cellcolor[HTML]{34FF34}Yes			   & \cellcolor[HTML]{FE0000}No			& \cellcolor[HTML]{34FF34}Yes						      \\ \hline
 \end{tabular}
@@
 GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FF3A3A}No  & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+Makecert		& \cellcolor[HTML]{FE0000}No	   & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No		   & \cellcolor[HTML]{34FF34}Yes				      \\ \hline
 \end{tabular}
@@
 
+\chapter{Makecert}
+
+\section{General}
+
+  \subsection{Type}
+Makecert can work with PKCS\#12 type files, however  default output is in \verb+.cer+ for certificate and \verb+.pvk+ for private key.
+To tie together key and certificate you need to combine them into PKCS\#12 type file with \verb+pvk2pfx+ tool (which is also part of Windows SDK).
+In addition to use the tool you need to start a Developer Command Prompt for Visual Studio (on Windows 10).
+\\ 
+In addition to that makecert is deprecated itself as cited on MSDN MakeCert site.
+  \subsection{View and information}
+Makecert does not allow user to view created certificates or any information about them whatsoever.
+  \subsection{License}
+It is free to use, falls under the Windows SDK.
+
+\section{Generation and signing of certificates}
+
+  \subsection{Keys, certificates and basic constraints}
+
+    \subsubsection{Generate keys}
+
+      \paragraph{Self-signed certificate}
+Generating key and self-signed certificate that can be used as CA is not straightforward with Makecert.
+\begin{verbatim}
+makecert -n "CN=Common Name, OU=Organization Unit, O=..." -cy [authority|end] \
+	 -a [sha256|sha384|sha512] -sv <key_file_name>.pvk -r \
+	 -len <int key_length> <cert_name>.cer
+\end{verbatim}
+
+Where -n sets credentials, -cy defines certificate type, -a chooses signature algorithm, -sv chooses name for file where the private key is stored, -r to create a self-signed certificate, -len for key length and without option choose the filename.
+
+After entering this command you will be prompted to enter private key file password.
+
+After creating certificate and private key file successfully to use self-signed certificate as a CA you need to join certificate file and private key into PKCS\#12 type file.
+This is made by using a pvk2pfx tool already implemented in Windows SDK.
+\begin{verbatim}
+pvk2pfx -spc <cert_file> -pvk <key_file>.pvk -pfx <pfx_file_name>.pfx \
+        [-pi <key_password> -po <pfx_password]
+\end{verbatim}
+
+-pi option is used if there is a password on key file, -po is desired pfx file password. If no password for pfx is given makecert defaults it to key file password.
+
+      \paragraph{Certificate Signing Request}
+It is not possible to create a CSR using Makecert.
+      \paragraph{Specify length}
+Length is specified by \verb+-len <int key_length>+ option.
+      \paragraph{Specify algorithm}
+To specify hash algorithm use \verb+-a [sha256|sha384|sha512]+ option. Supported are also SHA1 and MD5 but those are considered unsafe.
+
+To specify key algorithm you must change CSP.
+    \subsubsection{Basic constraints}
+
+      \paragraph{Specify Type}
+It is possible with \verb+-cy [authority|end]+ option.
+      \paragraph{Specify path length}
+Path length is specified by \verb+-h <int length>+ option while creating a certificate.
+  \subsection{Specifications}
+
+    \subsubsection{Certificate Signing Request signing}
+Not possible.
+    \subsubsection{Create combination of private key and signed chain}
+Not possible.
+    \subsubsection{Specify certificate validity}
+Defaults from date of creation until 2039, to change use \verb+-b <mm/dd/yyyy -> from> -e <mm/dd/yyyy -> until>+ option.
+Alternatively you can use \verb+-m <int months>+ option where you choose for how many months the certificate will be valid.
+    \subsubsection{Setting Subject Alternative Name for end certificates}
+Not possible.
+    \subsubsection{Support for Cryptographic Service Provider}
+There is support for CSP in makecert by using \verb+-sp <provider_name> -sy <provider_type>+ defines the CryptoAPI provider for subject.
+\section{Conversions}
+
+  \subsection{Exporting}
+
+    \subsubsection{Certificate or certificate chain from a file}
+Not possible.
+    \subsubsection{Private key only}
+Private key is stored and generated while generating a certificate but the type .pvk is uncommon.
+  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+Not possible.
+  \subsection{Importing certificates and keys into storage files}
+For importing of keys and certificates into PKCS\#12 file, use pvk2pfx as in generating self-signed part. There is just option to add 1 certificate and 1 private key into a file.
+
 %TEMPLATE FOR ALL OTHER TOOLS

### 2016-11-02 TEX/draft.tex
Changed ToC, repaired color in tables

@@
 \usepackage{graphicx}
+\usepackage[linktoc=all]{hyperref}
+
+\hypersetup{
+    colorlinks,
+    citecolor=black,
+    filecolor=black,
+    linkcolor=black,
+    urlcolor=black
+}
+
 \newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\} %used for better formating of some text
@@
 \author{Oliver Bodnár}
-\date{August 2016}
+\date{November 2016}
 
@@
 \multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
-OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
 Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
@@
 Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
-XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
-GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FF3A3A}No  & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
 Makecert		& \cellcolor[HTML]{FE0000}No	   & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No		   & \cellcolor[HTML]{34FF34}Yes				      \\ \hline

### 2016-11-16 TEX/draft.tex
Started Conclusion, ommited Notes -> Do a short Review and their + and - in a Conclusion part

@@
 \section{General}
-%TABLE START
 \begin{table}[h!]
@@
 GnuPG                   &        &                                                    &         &                                    \\ \hline
-Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
+Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win &\vert& OS X \\ \hline
 XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
@@
 Said keys/certificates can then be stored inside single .pfx file.
-  \cellcolor[HTML]{34FF34}Yes             
+
   \subsection{View and information}
@@
       \end{verbatim}
-      \cellcolor[HTML]{34FF34}Yes             
+
       \paragraph{Certificate Signing Request}
@@
 
+\section{Notes}
+
 \chapter{Keytool}
@@
 \end{verbatim}
-%unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found
 
@@
 
+\section{Notes}
+
 \chapter{GnuPG}
@@
   \subsection{Type}
-The type of file with which GnuPG works is a .gpg encoded in OpenPGP standard. As I understood the OpenPGP is competing standard to X509 standard.  
+GnuPG can make and view X509 Certificate Signing Requests
   \subsection{View and information}
@@
       \paragraph{Certificate Signing Request}
-
+Possible, but private key is not a part of output CSR.      
       \paragraph{Specify length}
@@
   \subsection{Importing certificates and keys into storage files}
+
+\section{Notes}
 
@@
 \begin{verbatim}
-# X.509 Certificate options
-#
-# DN options
-
-# The organization of the subject.
-organization = "Koko inc."
-
-# The organizational unit of the subject.
-unit = "sleeping dept."
-
-# The locality of the subject.
-# locality =
-
-# The state of the certificate owner.
-state = "Attiki"
-
-# The country of the subject. Two letter code.
-country = GR
-
-# The common name of the certificate owner.
-cn = "Cindy Lauper"
-
-# A user id of the certificate owner.
-#uid = "clauper"
-
-# Set domain components
-#dc = "name"
-#dc = "domain"
-
-# If the supported DN OIDs are not adequate you can set
-# any OID here.
-# For example set the X.520 Title and the X.520 Pseudonym
-# by using OID and string pairs.
-#dn_oid = "2.5.4.12 Dr."
-#dn_oid = "2.5.4.65 jackal"
-
-# This is deprecated and should not be used in new
-# certificates.
-# pkcs9_email = "none@none.org"
-
-# An alternative way to set the certificate's distinguished name directly
-# is with the "dn" option. The attribute names allowed are:
-# C (country), street, O (organization), OU (unit), title, CN (common name),
-# L (locality), ST (state), placeOfBirth, gender, countryOfCitizenship, 
-# countryOfResidence, serialNumber, telephoneNumber, surName, initials, 
-# generationQualifier, givenName, pseudonym, dnQualifier, postalCode, name, 
-# businessCategory, DC, UID, jurisdictionOfIncorporationLocalityName, 
-# jurisdictionOfIncorporationStateOrProvinceName,
-# jurisdictionOfIncorporationCountryName, XmppAddr, and numeric OIDs.
-
-#dn = "cn = Nikos,st = New\, Something,C=GR,surName=Mavrogiannopoulos,2.5.4.9=Arkadias"
-
-# The serial number of the certificate
-# Comment the field for a time-based serial number.
-serial = 007
-
-# In how many days, counting from today, this certificate will expire.
-# Use -1 if there is no expiration date.
-expiration_days = 700
-
-# Alternatively you may set concrete dates and time. The GNU date string 
-# formats are accepted. See:
-# http://www.gnu.org/software/tar/manual/html_node/Date-input-formats.html
-
-#activation_date = "2004-02-29 16:21:42"
-#expiration_date = "2025-02-29 16:24:41"
+
+dn = "cn=Common Name,st=State Name,C=CR,O=Organization,OU=OrganizationUnit,L=Locality"
+serial = <serial_nr>
+expiration_days = <int_days_from_now>
 
 # X.509 v3 extensions
-
-# A dnsname in case of a WWW server.
-#dns_name = "www.none.org"
-#dns_name = "www.morethanone.org"
-
-# An othername defined by an OID and a hex encoded string
-#other_name = "1.3.6.1.5.2.2 302ca00d1b0b56414e5245494e2e4f5247a11b3019a006020400000002a10f300d1b047269636b1b0561646d696e"
-#other_name_utf8 = "1.2.4.5.6 A UTF8 string"
-#other_name_octet = "1.2.4.5.6 A string that will be encoded as ASN.1 octet string"
-
-# Allows writing an XmppAddr Identifier
-#xmpp_name = juliet@im.example.com
-
-# Names used in PKINIT
-#krb5_principal = user@REALM.COM
-#krb5_principal = HTTP/user@REALM.COM
-
-# A subject alternative name URI
-#uri = "http://www.example.com"
-
-# An IP address in case of a server.
-#ip_address = "192.168.1.1"
-
-# An email in case of a person
-email = "none@none.org"
-
-# TLS feature (rfc7633) extension. That can is used to indicate mandatory TLS
-# extension features to be provided by the server. In practice this is used
-# to require the Status Request (extid: 5) extension from the server. That is,
-# to require the server holding this certificate to provide a stapled OCSP response.
-# You can have multiple lines for multiple TLS features.
-
-# To ask for OCSP status request use:
-#tls_feature = 5
+dns_name = "www.dns1.org"
+dns_name = "www.dns2.org"
+...
+
+ip_address = "192.168.1.1"
 
@@
 # Password when encrypting a private key
-#password = secret
-
-# An URL that has CRLs (certificate revocation lists)
-# available. Needed in CA certificates.
-#crl_dist_points = "http://www.getcrl.crl/getcrl/"
+password = secret
 
 # Whether this is a CA certificate or not
-#ca
-
-# Subject Unique ID (in hex)
-#subject_unique_id = 00153224
-
-# Issuer Unique ID (in hex)
-#issuer_unique_id = 00153225
-
-#### Key usage
-
-# The following key usage flags are used by CAs and end certificates
-
-# Whether this certificate will be used to sign data (needed
-# in TLS DHE ciphersuites). This is the digitalSignature flag
-# in RFC5280 terminology.
-signing_key
+ca
 
@@
 # keyCertSign flag in RFC5280 terminology.
-#cert_signing_key
-
-# Whether this key will be used to sign CRLs. The
-# cRLSign flag in RFC5280 terminology.
-#crl_signing_key
-
-# The keyAgreement flag of RFC5280. It's purpose is loosely
-# defined. Not use it unless required by a protocol.
-#key_agreement
-
-# The dataEncipherment flag of RFC5280. It's purpose is loosely
-# defined. Not use it unless required by a protocol.
-#data_encipherment
-
-# The nonRepudiation flag of RFC5280. It's purpose is loosely
-# defined. Not use it unless required by a protocol.
-#non_repudiation
-
-#### Extended key usage (key purposes)
-
-# The following extensions are used in an end certificate
-# to clarify its purpose. Some CAs also use it to indicate
-# the types of certificates they are purposed to sign.
-
-# Whether this certificate will be used for a TLS client;
-# this sets the id-kp-serverAuth (1.3.6.1.5.5.7.3.1) of 
-# extended key usage.
-#tls_www_client
-
-# Whether this certificate will be used for a TLS server;
-# This sets the id-kp-clientAuth (1.3.6.1.5.5.7.3.2) of 
-# extended key usage.
-#tls_www_server
-
-# Whether this key will be used to sign code. This sets the
-# id-kp-codeSigning (1.3.6.1.5.5.7.3.3) of extended key usage
-# extension.
-#code_signing_key
-
-# Whether this key will be used to sign OCSP data. This sets the
-# id-kp-OCSPSigning (1.3.6.1.5.5.7.3.9) of extended key usage extension.
-#ocsp_signing_key
-
-# Whether this key will be used for time stamping. This sets the
-# id-kp-timeStamping (1.3.6.1.5.5.7.3.8) of extended key usage extension.
-#time_stamping_key
-
-# Whether this key will be used for email protection. This sets the
-# id-kp-emailProtection (1.3.6.1.5.5.7.3.4) of extended key usage extension.
-#email_protection_key
-
-# Whether this key will be used for IPsec IKE operations (1.3.6.1.5.5.7.3.17).
-#ipsec_ike_key
-
-## adding custom key purpose OIDs
-
-# for microsoft smart card logon
-# key_purpose_oid = 1.3.6.1.4.1.311.20.2.2
-
-# for email protection
-# key_purpose_oid = 1.3.6.1.5.5.7.3.4
-
-# for any purpose (must not be used in intermediate CA certificates)
-# key_purpose_oid = 2.5.29.37.0
-
-### end of key purpose OIDs
-
-### Adding arbitrary extensions
-# This requires to provide the extension OIDs, as well as the extension data in
-# hex format. The following two options are available since GnuTLS 3.5.3.
-#add_extension = "1.2.3.4 0x0AAB01ACFE"
-
-# As above but encode the data as an octet string
-#add_extension = "1.2.3.4 octet_string(0x0AAB01ACFE)"
-
-# For portability critical extensions shouldn't be set to certificates.
-#add_critical_extension = "5.6.7.8 0x1AAB01ACFE"
+cert_signing_key
 
@@
 # and store them in the real certificate.
-#honor_crq_extensions
-
-# Alternatively only specific extensions can be copied.
-#honor_crq_ext = 2.5.29.17
-#honor_crq_ext = 2.5.29.15
+honor_crq_extensions
 
@@
 #path_len = 2
-
-# OCSP URI
-# ocsp_uri = http://my.ocsp.server/ocsp
-
-# CA issuers URI
-# ca_issuers_uri = http://my.ca.issuer
-
-# Certificate policies
-#policy1 = 1.3.6.1.4.1.5484.1.10.99.1.0
-#policy1_txt = "This is a long policy to summarize"
-#policy1_url = http://www.example.com/a-policy-to-read
-
-#policy2 = 1.3.6.1.4.1.5484.1.10.99.1.1
-#policy2_txt = "This is a short policy"
-#policy2_url = http://www.example.com/another-policy-to-read
-
-# Name constraints
-
-# DNS
-#nc_permit_dns = example.com
-#nc_exclude_dns = test.example.com
-
-# EMAIL
-#nc_permit_email = "nmav@ex.net"
-
-# Exclude subdomains of example.com
-#nc_exclude_email = .example.com
-
-# Exclude all e-mail addresses of example.com
-#nc_exclude_email = example.com
-
-# IP
-#nc_permit_ip = 192.168.0.0/16
-#nc_exclude_ip = 192.168.5.0/24
-#nc_permit_ip = fc0a:eef2:e7e7:a56e::/64
-
-# Options for proxy certificates
-#proxy_policy_language = 1.3.6.1.5.5.7.21.1
-
-# Options for generating a CRL
-
-# The number of days the next CRL update will be due.
-# next CRL update will be in 43 days
-#crl_next_update = 43
-
-# this is the 5th CRL by this CA
-# Comment the field for a time-based number.
-#crl_number = 5
-
-# Specify the update dates more precisely.
-#crl_this_update_date = "2004-02-29 16:21:42"
-#crl_next_update_date = "2025-02-29 16:24:41"
-
-# The date that the certificates will be made seen as
-# being revoked.
-#crl_revocation_date = "2025-02-29 16:24:41"
 \end{verbatim}
@@
 
+\part{Conclusion}
+
+\chapter{Tools Review}
+
+The main thing to understand is, that every tool has had its strong and weak points.
+Every should be used in complience with required properties of use.
+That can mean restrictions on used Operating System (e.g.
+customer has only access to Apple computers with OS X operating system), or for example restrictions how it should be used on Operating System (command line vs GUI programm).
+In the next part i will try to go over strengths and weaknesses of each tool that I have tested.
+
+Section{}
+
 \end{document}

### 2016-11-18 TEX/draft.tex
Added conclusion, finalized tables, started deleting content that is not supported by tools (If it is partially supported then not)

@@
 GnuPG                   &        &                                                    &         &                                      \\ \hline
-Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win &\vert& OS X \\ \hline
+Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win \vert OSX\\ \hline
 XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both         \\ \hline
@@
 GnuTLS                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
-Makecert               & \cellcolor[HTML]{34FF34}Yes					      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFFFFF}    & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+Makecert               & \cellcolor[HTML]{34FF34}Yes					      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFC702}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 \end{tabular}
@@
 \paragraph{Self-signed certificate}
-possibility of using 1 command to generate key pair and self-signed certificate
+Possibility of generating key pair and self-signed certificate
 
 \paragraph{Certificate Signing Request}
-possibility of using a command to generate key pair and certificate signing request to certificate authority.
+Possibility of using a command to generate key pair and certificate signing request to certificate authority.
 
 \paragraph{Specify length}
-possibility to specify the length of output key
+Possibility to specify the length of output key
 
 \paragraph{Specify algorithm}
-possibility to choose between different types of algorithms for key generation
+Possibility to choose between different types of algorithms for key generation
 
@@
 \paragraph{Specify Type}
-specify if generated certificate will belong to certificate authority or whether it will be end certificate
-
-\paragraph{Specify path length}
-specify the maximum length of certificate authority chain
+Specify if generated certificate will belong to certificate authority or whether it will be end certificate
+
+\paragraph{Specify Path Length}
+Specify the maximum length of certificate authority chain
 
@@
 Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
-XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & ???
-\\ \hline
-GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & ???	                                  & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
+XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
+GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{FE0000}No               & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
 Makecert	       & \cellcolor[HTML]{FE0000}No    &   \cellcolor[HTML]{FE0000}No	 	  & \cellcolor[HTML]{34FF34}Yes			   & \cellcolor[HTML]{FE0000}No			& \cellcolor[HTML]{34FF34}Yes						      \\ \hline
@@
 
+However for any other type of Key generating algorithm, it is better to create key separately. There are options to create a key in onecommand, but they are quirky.
+
       \paragraph{Certificate Signing Request}
@@
     \subsubsection{Certificate Signing Request signing}
-   SR signing can be done by CA created in openSSL by command
+CSR signing can be done by CA created in openSSL by command
 \begin{verbatim}
@@
 
-\section{Notes}
-
 \chapter{Keytool}
@@
 keytool -genkey -keyalg [RSA|DSA] -alias [alisaname] \
-        -keystore [keystore_file] -storepass [password] \
-        -validity [time] -keysize [length]
-\end{verbatim}
+        -keystore [keystore_file.jks] -storepass [password] \
+        -validity [days] -keysize [length]
+\end{verbatim}
+
+It should be noted that afterwards, when user is prompted to input First and Last name it is equal to Common Name parameter.
 
@@
       \paragraph{Specify length}
-Length is specified when generating keys, RSA support for up to 4096, DSA support from 512 up to 1024.
+Length is specified when generating keys, RSA support for up to 4096, DSA support from 512 up to 1024 as stated in manual, but i managed to create key lengths of bigger value whilst generating.
 
@@
 Algorithm is specified while generating key pair, currently support for DSA, RSA. EC is needed to be implemented.
+
+To choose signing algorithm use \verb+-sigalg+ option which can have values of \verb+[SHA1|MD5|SHA256|SHA512]with[RSA|DSA]+. This changes with change of Cryptographic service provider.
     \subsubsection{Basic constraints}
@@
     \subsubsection{Private key only}
-Exporting of private key only is not availiable in keytool.
+Exporting of private key only is not availiable directly in keytool. It is possible by changing keystore type to PKCS\#12 and then using other tool such as OpenSSL.
 
@@
 
-\section{Notes}
-
 \chapter{GnuPG}
@@
       \paragraph{Self-signed certificate}
-Generation of keys and self-signed certificate is not supported. In older versions it was possigle with \verb+gpgm+
+
       \paragraph{Certificate Signing Request}
@@
 Keystore Explorer allows to add both DNS and IP formats of SAN.
-    \subsubsection{Support for Cryptographic Service Provider}
-As Far as i know there is not support for using CSP.
 \section{Conversions}
@@
 Subject Alternative Names are specified in appropriate section under a Extensions tab.
-    \subsubsection{Support for Cryptographic Service Provider}
-As far as i know there is no support for CSP.
+
 \section{Conversions}
@@
 Possible by using export option, choosing in which format you want to export it.
+
     \subsubsection{Private key only}
 Exporting of private key only directly is availiable.
-  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-Conversion between PKCS\#12 and JKS is not possible.
+
   \subsection{Importing certificates and keys into storage files}
@@
 
-To define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512+ option while generating a certificate.
+To define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512]+ option while generating a certificate.
 
@@
 
-    \subsubsection{Support for Cryptographic Service Provider}
-GnuTLS does not have support for CSP.
 \section{Conversions}
@@
 In addition to that makecert is deprecated itself as cited on MSDN MakeCert site.
-  \subsection{View and information}
-Makecert does not allow user to view created certificates or any information about them whatsoever.
   \subsection{License}
@@
 
-      \paragraph{Certificate Signing Request}
-It is not possible to create a CSR using Makecert.
       \paragraph{Specify length}
@@
 
-    \subsubsection{Certificate Signing Request signing}
-Not possible.
-    \subsubsection{Create combination of private key and signed chain}
-Not possible.
     \subsubsection{Specify certificate validity}
@@
 Alternatively you can use \verb+-m <int months>+ option where you choose for how many months the certificate will be valid.
-    \subsubsection{Setting Subject Alternative Name for end certificates}
-Not possible.
     \subsubsection{Support for Cryptographic Service Provider}
@@
 
-    \subsubsection{Certificate or certificate chain from a file}
-Not possible.
     \subsubsection{Private key only}
 Private key is stored and generated while generating a certificate but the type .pvk is uncommon.
-  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-Not possible.
   \subsection{Importing certificates and keys into storage files}
@@
 
-Section{}
+\section{OpenSSL}
+It is a great command line tool, can work with PEM, DES and PKCS\#12 files.
+Strong point is a easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in man pages and also a O'REILLY's OpenSSL book.
+Another strong point is configuration, which can be done in file. I tested it with creation of appropriate directories and configs.
+
+Tested under Fedora 21, OpenSSL version 1.0.1k-fips
+
+\section{Keytool}
+Keytool is the only command line tool using Java Keystore to store keys and certificates, which i consider it main strong point.
+By default the CSP is \verb+java.security.provider+ which allows RSA and DSA options and SHA-1,MD5,SHA-256 and SHA-512 hash algorithms.
+This Changes when choosing other Cryptographic Service Provider.
+Working with it is quite easy and support for exporting as PKCS\#12 is usefull addition.
+
+Tested under Fedora 21 and OpenSUSE 42.1, openjdk version 1.8.0\_65
+
+\section{GnuPG}
+To be added.
+
+\section{Keystore Explorer}
+A great GUI tool for when you need to work with different types of Java Keystore files for example supports Bouncy Castle implementation.
+Even though CSP support is not implicit, there are different choices already implemented.
+Those can be viewed under \verb+Help->Security Providers+ tab.
+
+Main downfall is that keys of length greater than 4096 take longer to generate (notably RSA of length 16192, it took almost 2 hours to generate).
+
+Tested under MS Windows 10 version 1607 Build 14393.447, Keystore Explorer version 5.2.1
+
+\section{XCA}
+XCA is a great GUI tool that can work with PEM, DER and PKCS\#12 type of files.
+Main advantage is simplicity and ammount of options, basic options are readily availiable as a button.
+There are many exporting options, for example PEM encoded certificate file with PKCS\#8 encrypted key file.
+Although there is no CSP support, its ease of use makes it a great testing tool.
+
+Tested under Windows 10 version 1607 Build 14393.447 and Fedora 21, XCA version 1.3.2 using OpenSSL version 1.0.2d
+
+\section{GnuTLS}
+Command line tool, availiable only under Linux.
+Very friendly to use, many different options in configuration file.
+Great support for different key and hash algorithm types.
+Supports key lengths of higher values (greater than 4096 RSA for example).
+Its weaknesses are no support for CSP and availibility only under LINUX Operating Systems.
+
+Tested under Fedora 21, certtool version 3.3.16
+\section{Makecert}
+Command line tool, not to be used in production code since microsoft has deprecated it.
+Very unfriendly to use and only way to use it is to download a whole Windows SDK and use it with Visual Studio console.
+Overall it shouldn't be used.
+
+Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298
+\section{New-SelfSignedCertificate}
+TBA - error of access denied, need fix.
 

### 2016-11-24 TEX/draft.tex
Finalization of project

@@
 
-\title{Report on Certificate Tools}
+\title{Review and comparison of tools for manageing X.509 type keys and certificates}
 \author{Oliver Bodnár}
@@
 
+\part{Introduction}
+
+Primary goal of this work is to compare and review some of the basic functionalities \textit{(e.g.
+generation of keys and certificates, ability to create a certificate signing request,...)} of tools working with keys and certificates in X509 public key infrastructure.
+Comparison of tools is necessary to understand that ability of a tool to do everything that was tested does not mean that it is the best tool to use in every situation.
 \part{Overview}
@@
 \begin{adjustbox}{max width=\textwidth}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-                        & \multicolumn{4}{c|}{General}                                                                                 \\ \cline{2-5} 
-\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System                     \\ \hline
-OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both         \\ \hline
-Keytool                 & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both         \\ \hline
-GnuPG                   &        &                                                    &         &                                      \\ \hline
-Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win \vert OSX\\ \hline
-XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both         \\ \hline
-GnuTLS                  & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX        \\ \hline
-Makecert                & PKCS12 & \cellcolor[HTML]{FE0000}No			      & Public  & \cellcolor[HTML]{FFC702}Windows      \\ \hline
+                              & \multicolumn{5}{c|}{General}                                                                                   \\ \cline{2-6} 
+\multirow{-2}{*}{Tools}       & Type   & View information about certificate                 & License & Operating System                        & Tool Type           \\ \hline
+OpenSSL                       & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both            & Command Line        \\ \hline
+Keytool                       & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both            & Command Line        \\ \hline
+GnuPG                         & None   & \cellcolor[HTML]{FE0000}No                         & Public  & \cellcolor[HTML]{34FF34}Both            & Command Line        \\ \hline
+Keystore Explorer             & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win $\vert$ OSX & Graphical Interface \\ \hline
+XCA                           & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both            & Graphical Interface \\ \hline
+GnuTLS                        & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX           & Command Line        \\ \hline
+Makecert                      & PKCS12 & \cellcolor[HTML]{FE0000}No			    & Public  & \cellcolor[HTML]{FFC702}Windows         & Command Line        \\ \hline
+Windows PowerShell PKI Module & PKCS12 & \cellcolor[HTML]{34FF34}Yes			    & Public  & \cellcolor[HTML]{FFC702}Windows         & Command Line        \\ \hline
 \end{tabular}
@@
 
-\subsection{View and information}
-This section shows whether it is possible to view certificates or keys and additional information.
-Yes means that at least viewing is supported while not necessary meaning possibility of viewing more information about certificate.
-
+\subsection{View information about certificate}
+This section shows whether it is possible to view information certificates and keys and additional information. 
+    \begin{itemize}
+     \item \textit{Yes} - viewing information about certificates and keys is availiable. This includes length, used algorithm, fingerprint.
+     \item \textit{No}  - tool does not have an option to view any information about certificates or keys.
+    \end{itemize}
 \subsection{License}
@@
 Public means that license is not requiered for use in production code but does not mean that it should be used as such.
-Definition if it is advised to use said tool in production code or only in testing enviroment will be talked about in the next chapter under each tool.
+Definition if it is advised to use said tool in production code or only in testing enviroment will be talked about in next chapters under each tool.
 
@@
 Both means that it is implemented under UNIX like systems and Windows systems.
-Otherwise the Operating System is defined (Windows | UNIX).
-
+Otherwise the Operating System is defined (Windows $\vert$ UNIX).
+
+\subsection{Tool Type}
+This section shows what type of input is used in Tool. 
+\begin{itemize}
+\item \textit{Command Line} - tool is used with commands on some sort of console (PowerShell, Command Prompt, Terminal)
+\item \textit{Graphical Interface} - tool is used with Graphical Interface, main interaction is by user using mouse
+\end{itemize}
 \newpage
@@
                               & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7}
-\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
+\multirow{-2}{*}{Tool}        & \begin{tabular}[c]{@{}c@{}}     self-signed certificate\end{tabular} &   CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
 OpenSSL                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 Keytool                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
-GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
+GnuPG                         & \cellcolor[HTML]{FE0000}No                                           & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000} No & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
 Keystore explorer             & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
@@
 Makecert                      & \cellcolor[HTML]{34FF34}Yes					     & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFC702}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+Windows PowerShell PKI Module & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
 \end{tabular}
@@
 \paragraph{Self-signed certificate}
-Possibility of generating key pair and self-signed certificate
+The tool is capable of generating private key and corresponding self-signed certificate
 
@@
 \paragraph{Specify algorithm}
-Possibility to choose between different types of algorithms for key generation
+Possibility to choose between different types of algorithms for key generation and message digest\textit{(hash)}.
 
@@
 Keytool                       & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
-GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
+GnuPG                         & \cellcolor[HTML]{FE0000}No    & \cellcolor[HTML]{FE0000}No               & \cellcolor[HTML]{FE0000}No                     & \cellcolor[HTML]{FE0000}No                 & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
 Keystore explorer             & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
@@
 Makecert	              & \cellcolor[HTML]{FE0000}No    & \cellcolor[HTML]{FE0000}No	 	 & \cellcolor[HTML]{34FF34}Yes	               & \cellcolor[HTML]{FE0000}No                 & \cellcolor[HTML]{34FF34}Yes              		                          \\ \hline
+Windows PowerShell PKI Module & \cellcolor[HTML]{FE0000}No    & \cellcolor[HTML]{FE0000}No	         & \cellcolor[HTML]{34FF34}Yes	               & \cellcolor[HTML]{34FF34}Yes	            & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
 \end{tabular}
@@
 \paragraph{Certificate Signing Request signing}
-possibility of signing a certificate signing request with certificate authority's key
+Possibility of signing a certificate signing request with certificate authority's key
 
 \paragraph{Create combination of private key and signed chain}
-possibility of generating private key and chain signed by certificate authority that will be outputed to a single file
+Possibility of generating private key and chain signed by certificate authority that will be outputed to a single file
 
 \paragraph{Specify certificate validity}
-possibility of choosing how long will the certificate be valid. This should be done by certificate authority.
+{ossibility of choosing how long the certificate will be valid. This should be done by certificate authority.
 
 \paragraph{Setting Subject Alternative Name for end certificates}
-possibility of choosing Subject Alternative Name for end certificates. That should be done by IP's or DNS addresses.
+Possibility of choosing Subject Alternative Name for end certificates. That should be done by IP's or DNS addresses.
 
 \paragraph{Support for Cryptographic Service Provider}
-whether the use, choosing and changing of Cryptographic Service Provider is supported.
+Whether the use, choosing and changing of Cryptographic Service Provider is supported.
 
@@
                               & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
-\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
+\multirow{-3}{*}{Tools}       & Certificate or chain from file   & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Import certificate and\\ private key into a file\end{tabular}} \\ \hline
 OpenSSL                       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
-Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
-GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
+Keytool                       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
+GnuPG                         & \cellcolor[HTML]{FE0000}No       & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No              & \cellcolor[HTML]{FE0000}No                                       \\ \hline
 Keystore explorer             & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
@@
 Makecert		      & \cellcolor[HTML]{FE0000}No	   & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No		   & \cellcolor[HTML]{34FF34}Yes				      \\ \hline
+Windows PowerShell PKI Module & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
 \end{tabular}
@@
 \subsubsection{Private key only}
-Possibility of extracting private key from tool's file storage type of choice.
+Possibility of extracting private key only from a certificate.
 
@@
 \section{General}
-
+Tested under Fedora 21, OpenSSL version 1.0.1k-fips
   \subsection{Type}
-  OpenSSL uses PKCS12 to store keys and or certificates.
-Certificates and keys  made in OpenSSL however are being made into PEM or DER encoded file.
-Said keys/certificates can then be stored inside single .pfx file.
-
-  \subsection{View and information}
+  OpenSSL uses PKCS12 to store keys and certificates.
+Certificates and keys generated in OpenSSL are however being made into PEM or DER encoded file.
+PEM or DER encoded keys and certificates can then be stored inside single PKCS\#12 file.
+
+  \subsection{View information}
 
@@
   \end{verbatim}
-certfile option is used only if importing more certificates into a single PKCS\#12 file is wanted.
+\verb+-certfile+ option is used only if importing more certificates into a single PKCS\#12 file is wanted.
 
@@
       \paragraph{Specify path length}
-Specifying of path length is made by setting a \verb+<maxCheinLengthInteger>+ to desired value (e.g. if generated certificate should be used only for generating end certificates the value is 0)
+Specifying of path length is made by setting a \verb+<maxChainLengthInteger>+ to desired value (e.g. if generated certificate should be used only for generating end certificates the value is 0)
   \subsection{Specifications}
@@
 
+Tested under Fedora 21 and OpenSUSE 42.1, openjdk version 1.8.0\_65
+
   \subsection{Type}
@@
   \subsection{View and information}
+When viewing certificates, command for PEM and DER certificates will return errors with command for PKCS\#12 amd JKS files.
+
 To view information about PEM or DER encoded certificate use:
@@
 Viewing Public key part of certificate is not availiable in keytool.
+
   \subsection{License}
@@
 \begin{verbatim}
-keytool -genkey -keyalg [RSA|DSA] -alias [alisaname] \
+keytool -genkey -keyalg [RSA|DSA] -alias [aliasname] \
         -keystore [keystore_file.jks] -storepass [password] \
@@
 \end{verbatim}
-Where you need to set -keyalg -alias and -keystore as chosen when generating key pair earlier.
+Where you need to set \verb+-keyalg -alias+ and \verb+-keystore+ as chosen when generating key pair earlier.
 
@@
     \subsubsection{Create combination of private key and signed chain}
-You can import a key pair into a Java KeyStore file along with signed chain if the signed chain is provided and a CA certificate is imported into said Java Keystore.
+You can import a key pair along with a signed chain if it is provided in PKCS\#12 file format.
+\begin{verbatim}
+keytool -importkeystore -srckeystore [pkcs12_file].[pfx|p12] \
+        -srcstoretype pkcs12 -destkeystore <output_name>.jks
+\end{verbatim}
+
     \subsubsection{Specify certificate validity}
-Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option.
+Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option. But changed by CA when being signed.
 
@@
 
+Tested under Fedora 21, OpenSUSE 42.1, Debian Wheezy, gpgsm (GnuPG) 2.0.29, libgcrypt 1.6.3, libksba 1.3.2 and also MS Windows 10 version 1607 Build 14393.447, MS Windows 8.1 Pro 6.3.9600, gpgsm (GnuPG) 2.0.30 (Gpg4win 2.3.3), libgcrypt 1.6.6, libksba 1.3.4
+
   \subsection{Type}
 GnuPG can make and view X509 Certificate Signing Requests
-  \subsection{View and information}
 
@@
 
-      \paragraph{Self-signed certificate}
-
       \paragraph{Certificate Signing Request}
-Possible, but private key is not a part of output CSR.     
-      \paragraph{Specify length}
-
-      \paragraph{Specify algorithm}
-
-    \subsubsection{Basic constraints}
-
-      \paragraph{Specify Type}
-
-      \paragraph{Specify path length}
-
-  \subsection{Specifications}
-
-    \subsubsection{Certificate Signing Request signing}
-
-    \subsubsection{Create combination of private key and signed chain}
-
-    \subsubsection{Specify certificate validity}
-
-    \subsubsection{Setting Subject Alternative Name for end certificates}
-
-    \subsubsection{Support for Cryptographic Service Provider}
-
-\section{Conversions}
-
-  \subsection{Exporting}
-
-    \subsubsection{Certificate or certificate chain from a file}
-
-    \subsubsection{Private key only}
-
-  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-
-  \subsection{Importing certificates and keys into storage files}
-
-\section{Notes}
-
-%KEYSTORE EXPLORER PART 
+Possible by using \verb+gpgsm --gen-key > <output_file>+ command, but private key is not a part of output CSR.
+
 \chapter{Keystore Explorer}
@@
 \section{General}
+
+Tested under MS Windows 10 version 1607 Build 14393.447, Keystore Explorer version 5.2.1
 
@@
 \end{figure}
+
 \subsection{View and information}
 You can view certificates and additional information with Keystore Explorer, view public and private key parts of certificates and other info such as subject alternative names by right clicking a certificate and choosing viable option from View option.
+
   \subsection{License}
@@
 Then you can choose all the other options such as Basic Constraints and Subject Alternative Name.
+\textit{(Figure 5.3)}
+
 \begin{figure}[!ht]
@@
       \paragraph{Certificate Signing Request}
-It is possible to make Certificate Signing Request in Keystore Explorer. Simply generate key pair certificate and then right click the generated certificate and choose Generate CSR option.
+It is possible to make Certificate Signing Request in Keystore Explorer.
+Simply generate key pair certificate and then right click the generated certificate and choose Generate CSR option.
+\textit{(Figure 5.4)}
+
 \begin{figure}[!ht]
@@
 Length is specified at the moment of key pair generation.
+
       \paragraph{Specify algorithm}
 Algorithm of keys is specified when generating keys and the certificate hash function is chosen by certificate authority.
+
     \subsubsection{Basic constraints}
+
 \begin{figure}[!ht]
@@
 Specifying type is made while generating keys and certificate by changing v3 portion when asked during generation.
+
       \paragraph{Specify path length}
-Specifying of max path length is made also by changing v3 part of x509 certificate during generation under Basic Constraints type.
+Specifying of max path length is made also by changing v3 part of x509 certificate during generation under Basic Constraints type.\textit{(Figure 5.5)}
+
   \subsection{Specifications}
@@
     \subsubsection{Certificate Signing Request signing}
-To sign a Certificate Signing Request simply right-click a Certificate Authority certificate and use the sign->CSR option.
-Then you need to import CA response that was generated in a desired place into a certificate from which the CSR was generated.
+To sign a Certificate Signing Request simply right-click a Certificate Authority certificate and use the \verb+sign->CSR+ option.
+Then you need to import CA response that was generated and saved in a desired place into a certificate from which the CSR was generated.
+\textit{(Figure 5.6)}
 
@@
     \subsubsection{Create combination of private key and signed chain}
-To create combination of private key simply generate new key pair certificate, export private key part, import it back and then import to new certificate of private key a trusted chain.
+To create combination of private key and signed chain simply generate new key pair certificate, export private key part, import it back and then import to new certificate of private key a trusted chain.
 
@@
 Desired duration of certificate validity is asked during generation, but given whilst signing a Certificate Signing Request by Certificate Authority
+
     \subsubsection{Setting Subject Alternative Name for end certificates}
@@
 Keystore Explorer allows to add both DNS and IP formats of SAN.
+
 \section{Conversions}
@@
 It is possible to export a certificate or certificate chain from a keystore by simply right-clicking the chosen certificate and chosing export option.
+
     \subsubsection{Private key only}
-It is possible to export a private key from a keystore by simply right-clicking the chosen certificate and chosing export->private key option.
+It is possible to export a private key from a keystore by simply right-clicking the chosen certificate and chosing \verb+export->private key+ option.
 
@@
   \subsection{Importing certificates and keys into storage files}
-It is possible to import a certificate and/or key by chosing Import option.
+It is possible to import a certificates and keys by chosing Import option.
 
@@
 
+Tested under Windows 10 version 1607 Build 14393.447 and Fedora 21, XCA version 1.3.2 using OpenSSL version 1.0.2d
+
   \subsection{Type}
-XCA works with PKCS\#12 type files, but it is neccessary to make theirs database file which stores and to which you can import certificates, certificate signing requests or keys.
+XCA works with PKCS\#12 type files, but it is neccessary to make their database file which stores and to which you can import certificates, certificate signing requests or keys.
   \subsection{View and information}
@@
   \subsection{License}
-XCA is under BSD License - it is free to use for testing and also commercialy.
+XCA is distributed under BSD License - it is free to use for testing and also commercialy.
 
@@
 You can generate key pair by itself and then use it for generation of certificate.
-If you do not generate key in advance there is option to generate new key whilst generating a certificate.
-To generate a certificate click on Certificates tab and press New Certificate.
+If you do not generate key in advance there is option to generate new key whilst generating a certificate.\textit{{Figure 6.1}} To generate a certificate click on Certificates tab and press New Certificate.
 There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm (\verb+MD5|SHA1|SHA224|SHA256|SHA384|SHA512|RIPEMD160+).
@@
 For certificate to be accepted by all operating systems you need to choose \verb+Digital Signature & Key Agreement & Certificate Sign+ under Key usage tab.
+\textit{(Figure 6.2)}
 \begin{figure}[!ht]
@@
 \begin{figure}[!ht]
- \caption{Specify use}
+ \caption{Specify usage}
  \centering
@@
       \paragraph{Certificate Signing Request}
-Certificate Signing Request is generated simmilarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
+Certificate Signing Request is generated similarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
 \begin{figure}[!ht]
@@
     \subsubsection{Certificate Signing Request signing}
-To sign CSR you must have a CA certificate already in XCA's database.
-If a CA is availiable then you can sign CSR by using New Certificate option under Certificates tab or right click on CSR under Certificate signing requests tab and choose Sign option.
+To sign CSR you must have a CA certificate already in XCA's database. If a CA is availiable then you can sign CSR by:
+
+\begin{enumerate}
+\item using New Certificate option under Certificates tab 
+\item right click on CSR under Certificate signing requests tab and choose Sign option. 
+\end{enumerate}
 Both options are equivalent.
+
     \subsubsection{Create combination of private key and signed chain}
@@
 Subject Alternative Names are specified in appropriate section under a Extensions tab.
+\textit{(Figure 6.5)}
 
@@
   \subsection{Importing certificates and keys into storage files}
-Certificates and keys can be Exported and imported to/from PKCS or PEM type files.
+Certificates and keys can be Exported and imported to/from PKCS\#12 or PEM type files.
 
@@
 \section{General}
+
+Tested under Fedora 21, certtool version 3.3.16
 
@@
       \paragraph{Self-signed certificate}
-To generate a self-signed certificate it is needed to generate a a private key. Generating of key is done by following command:
+To generate a self-signed certificate it is needed to generate a private key first. This is done by following command:
 \begin{verbatim}
@@
 
-More options when generating self-signed certificate (or a CSR) you need to create a config file which has structure as follows (copied from a man page):
-\begin{verbatim}
-
-dn = "cn=Common Name,st=State Name,C=CR,O=Organization,OU=OrganizationUnit,L=Locality"
-serial = <serial_nr>
-expiration_days = <int_days_from_now>
-
-# X.509 v3 extensions
-dns_name = "www.dns1.org"
-dns_name = "www.dns2.org"
-...
-
-ip_address = "192.168.1.1"
-
-# Challenge password used in certificate requests
-challenge_password = 123456
-
-# Password when encrypting a private key
-password = secret
-
-# Whether this is a CA certificate or not
-ca
-
-# Whether this certificate will be used to encrypt data (needed
-# in TLS RSA ciphersuites). Note that it is preferred to use different
-# keys for encryption and signing. This is the keyEncipherment flag
-# in RFC5280 terminology.
-encryption_key
-
-# Whether this key will be used to sign other certificates. The
-# keyCertSign flag in RFC5280 terminology.
-cert_signing_key
-
-# When generating a certificate from a certificate
-# request, then honor the extensions stored in the request
-# and store them in the real certificate.
-honor_crq_extensions
-
-# Path length contraint. Sets the maximum number of
-# certificates that can be used to certify this certificate.
-# (i.e. the certificate chain length)
-#path_len = -1
-#path_len = 2
-\end{verbatim}
+More options when generating self-signed certificate (or a CSR) you need to create a config file which has structure as is in appendix \textit{GnuTLS.cfg} 
+For whole list of options in a config file look up \verb+man certtol+.
 
@@
 
-when not using template it uses default values 
-%need to find out what those are
+when not using template it asks for:
+\begin{itemize}
+\item Common Name, Organizational Unit, Organization, ...
+\item Subject's domain component
+\item Subject Alternative Name
+\item If the certificate will be CA
+\item What the certificate will be used for \textit{(signing $\vert$ encryption)}
+\item Whether the certificate will be TLS web client/server certificate
+\end{itemize}
+
+\pagebreak
+
       \paragraph{Specify length}
+
 Length is specified when generating keys by \verb+--sec-param=[low|legacy|medium|high|ultra]+ where length is determined by alias and algorithm.
-For RSA:
-\begin{verbatim}
-low    = 1024 bit
-legacy = 1776 bit
-medium = 2048 bit
-high   = 3072 bit
-ultra  = 15424 bit
-\end{verbatim}
-For DSA:
-\begin{verbatim}
-low    = 1024 bit
-legacy = 2048 bit
-medium = 2048 bit
-high   = 3072 bit
-ultra  = 3072 bit
-\end{verbatim}
-For ECDSA:
-\begin{verbatim}
-low    = 160 bit
-legacy = 192 bit
-medium = 224 bit
-high   = 256 bit
-ultra  = 512 bit
-\end{verbatim}
+
+\begin{table}[]
+\centering
+\caption{Bit length of security parameter options}
+\label{my-label}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+               & \textbf{low}      & \textbf{legacy}   & \textbf{medium}   & \textbf{high}     & \textbf{ultra}     \\ \hline
+\textbf{RSA}   & \textit{1024 bit} & \textit{1776 bit} & \textit{2048 bit} & \textit{3072 bit} & \textit{15424 bit} \\ \hline
+\textbf{DSA}   & \textit{1024 bit} & \textit{2048 bit} & \textit{2048 bit} & \textit{3072 bit} & \textit{3072 bit}  \\ \hline
+\textbf{ECDSA} & \textit{160 bit}  & \textit{192 bit}  & \textit{224 bit}  & \textit{256 bit}  & \textit{512 bit}   \\ \hline
+\end{tabular}
+\end{table}
 
@@
 Validity is specified by changing cert.cfg file used while generating a certificate, the part \verb+expiration_days = <value>+
-Alternatively, you cen set NOT BEFORE and NOT AFTER times by changing \verb+activation_date = <NOT_BEFORE_STRING>+ and \verb+expiration_date = <NOT_AFTER_STRING>+ where the times are written in GNU date string format.
+Alternatively, you cen set \verb+NOT BEFORE+ and \verb+NOT AFTER+ times by changing \verb+activation_date = <NOT_BEFORE_STRING>+ and \verb+expiration_date = <NOT_AFTER_STRING>+ where the times are written in GNU date string format.
 
     \subsubsection{Setting Subject Alternative Name for end certificates}
-SAN is set by adding options to cert.cfg :
+SAN is set by adding options to cert.cfg
 \begin{verbatim}
@@
 It is not possible to export private key only, however for proper use of GnuTLS keys need to be stored on drive or imported to PKCS\#12 file.
-  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-Not possible.
   \subsection{Importing certificates and keys into storage files}
-Possible. - need to run up some facts.
+Possible.
 
@@
 \section{General}
+
+Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298
 
@@
 
-Where -n sets credentials, -cy defines certificate type, -a chooses signature algorithm, -sv chooses name for file where the private key is stored, -r to create a self-signed certificate, -len for key length and without option choose the filename.
+Where:
+\begin{itemize}
+\item \verb+-n+ sets credentials
+\item \verb+-cy+ defines certificate type
+\item \verb+-a+ chooses signature algorithm
+\item \verb+-sv+ chooses name for file where the private key is stored
+\item \verb+-r+ to create a self-signed certificate
+\item \verb+-len+ for key length and without option choose the filename.
+\end{itemize}
 
@@
 
--pi option is used if there is a password on key file, -po is desired pfx file password. If no password for pfx is given makecert defaults it to key file password.
+Where:
+\begin{itemize}
+\item \verb+-pi+ option is used if there is a password on key file
+\item \verb+-po+ is desired pfx file password. If no password for pfx is given makecert defaults it to key file password.
+\end{itemize}
 
@@
 It is possible with \verb+-cy [authority|end]+ option.
+
       \paragraph{Specify path length}
 Path length is specified by \verb+-h <int length>+ option while creating a certificate.
+
   \subsection{Specifications}
@@
 Defaults from date of creation until 2039, to change use \verb+-b <mm/dd/yyyy -> from> -e <mm/dd/yyyy -> until>+ option.
+
 Alternatively you can use \verb+-m <int months>+ option where you choose for how many months the certificate will be valid.
+
     \subsubsection{Support for Cryptographic Service Provider}
@@
 Private key is stored and generated while generating a certificate but the type .pvk is uncommon.
+
   \subsection{Importing certificates and keys into storage files}
@@
 
-%TEMPLATE FOR ALL OTHER TOOLS
-\chapter{Tool Page Template}
+\chapter{Windows PowerShell PKI Module}
+
+Tested under MS Windows 10 version 14393.447
 
@@
 
+It should be noted that to be able to write into internal certificate storage, the PowerShell needs to be run as Administrator.
   \subsection{Type}
-
+Windows PowerShell PKI Module works with Windows internal certificate storage but is able to export certificates in PKCS\#12 and DER formats. 
   \subsection{View and information}
-
+To view information about certificates use \verb+Get-ChildItem -Path <path_to_cert>+ command where \verb+<path_to_cert>+ usually begins with \verb+Cert:\+ option.
+
+This commands howeve shows only thumbprint of certificate and a \verb+dns.name+. 
   \subsection{License}
+License is Public, but working Microsoft Windows OS with PowerShell installed is needed.
 
@@
       \paragraph{Self-signed certificate}
-
-      \paragraph{Certificate Signing Request}
-
-      \paragraph{Specify length}
-
-      \paragraph{Specify algorithm}
-
-    \subsubsection{Basic constraints}
-
-      \paragraph{Specify Type}
-
-      \paragraph{Specify path length}
+To generate self-signed certificate use 
+\begin{verbatim}
+New-SelfSignedCertificate [-Provider <String>] -Path <storage_path> -DnsName "<cert_name>" 
+\end{verbatim}
+
+Where \verb+<cert_name>+ is used as Common Name for certificate.
 
@@
 
-    \subsubsection{Certificate Signing Request signing}
-
-    \subsubsection{Create combination of private key and signed chain}
-
-    \subsubsection{Specify certificate validity}
-
     \subsubsection{Setting Subject Alternative Name for end certificates}
 
+If \verb+-DnsName <cert_name>+ is used as list of strings \textit{("dns1","dns2","dns3",...)} where \verb+dns2+ and latter are used as a Subject Alternative Name.
+
     \subsubsection{Support for Cryptographic Service Provider}
+Change of Cryptographic Service Provider is made by using \verb+-Provider <String>+ option.
 
@@
     \subsubsection{Certificate or certificate chain from a file}
-
-    \subsubsection{Private key only}
-
-  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
+Exporting of certificates is done by sequence:
+\begin{verbatim}
+$mypwd = Convert-To-SecureString -String "<password>" -Force -AsPlainText
+Get-ChildItem -Path <path> | Export-PfxCertificate -FilePath <where_to_store> \
+              [-ChainOption EndEntityCertOnly] [-Noproperties] -Password $mypwd
+\end{verbatim}
+
+Where:
+\begin{itemize}
+\item \verb+<password>+ will be password to created PKCS\#12 file as it is needed to export certificates and also needs to be of SecureString type.
+\item \verb+<path>+ can be:
+\begin{enumerate}
+\item Path to certificate - only a specified certificate will be exported
+\item Directory containing certificates \textit{e.g. Cert:{\textbackslash}LocalMachine{\textbackslash}My} - It will print all certificates into a single file
+\end{enumerate}
+\item \verb+<where_to_store>+ is location where the file will be saved.
+\item \verb+[-ChainOption EndEntityCertOnly]+ if used only End certificates will be outputed and certificate chain will be ommited.
+\item \verb+[-Noproperties]+ no additional properties will be printed out.
+\end{itemize}
 
   \subsection{Importing certificates and keys into storage files}
+It is possible as exporting a certificate into PKCS\#12 file.
 
@@
 
-Tested under Fedora 21, OpenSSL version 1.0.1k-fips
-
 \section{Keytool}
@@
 
-Tested under Fedora 21 and OpenSUSE 42.1, openjdk version 1.8.0\_65
-
 \section{GnuPG}
-To be added.
+Tool that can only make end certificates for authentication, CSR is PEM encoded and does not hold generated private key inside.
+Unreliable as it has been tested on 5 different Operating Systems and worked only on clean install of Windows 8.1.
 
@@
 Main downfall is that keys of length greater than 4096 take longer to generate (notably RSA of length 16192, it took almost 2 hours to generate).
-
-Tested under MS Windows 10 version 1607 Build 14393.447, Keystore Explorer version 5.2.1
 
@@
 
-Tested under Windows 10 version 1607 Build 14393.447 and Fedora 21, XCA version 1.3.2 using OpenSSL version 1.0.2d
-
 \section{GnuTLS}
@@
 Supports key lengths of higher values (greater than 4096 RSA for example).
-Its weaknesses are no support for CSP and availibility only under LINUX Operating Systems.
-
-Tested under Fedora 21, certtool version 3.3.16
+Its weaknesses are no support for CSP and availibility only under UNIX like Operating Systems.
+
 \section{Makecert}
@@
 
-Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298
-\section{New-SelfSignedCertificate}
-TBA - error of access denied, need fix.
+\section{Windows PowerShell PKI Module}
+PowerShell Module on Windows Operating Systems, much easier to use and generate new certificates.
+Downside is, that certificates made by it are RSAwithSHA256 2048bit and that can only be changed with change of Cryptographic Service Provider.
+It has replaced deprecated Makecert command line tool.
 

### 2016-11-24 TEX/draft.tex
Noticed mistake in OS part of GnuTLS table

@@
 XCA                           & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both            & Graphical Interface \\ \hline
-GnuTLS                        & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX           & Command Line        \\ \hline
+GnuTLS                        & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}UNIX            & Command Line        \\ \hline
 Makecert                      & PKCS12 & \cellcolor[HTML]{FE0000}No			    & Public  & \cellcolor[HTML]{FFC702}Windows         & Command Line        \\ \hline

### 2016-11-25 TEX/draft.tex
lists in overview, finalized Conclusion with best tools mentioned.

@@
 \multirow{-2}{*}{Tools}       & Type   & View information about certificate                 & License & Operating System                        & Tool Type           \\ \hline
-OpenSSL                       & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both            & Command Line        \\ \hline
-Keytool                       & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both            & Command Line        \\ \hline
-GnuPG                         & None   & \cellcolor[HTML]{FE0000}No                         & Public  & \cellcolor[HTML]{34FF34}Both            & Command Line        \\ \hline
+OpenSSL                       & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}All             & Command Line        \\ \hline
+Keytool                       & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}All             & Command Line        \\ \hline
+GnuPG                         & None   & \cellcolor[HTML]{FE0000}No                         & Public  & \cellcolor[HTML]{34FF34}All             & Command Line        \\ \hline
 Keystore Explorer             & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win $\vert$ OSX & Graphical Interface \\ \hline
-XCA                           & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both            & Graphical Interface \\ \hline
+XCA                           & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}All             & Graphical Interface \\ \hline
 GnuTLS                        & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}UNIX            & Command Line        \\ \hline
@@
 \subsection{Type}
-This section defines type of storage file in which the certificates or keys are saved. Most common are PKCS\#12 (.pfx and .p12 extentions) and JKS (Java KeyStore).
+This section defines type of storage file in which the certificates or keys are saved. 
+Options are:
+    \begin{itemize}
+     \item \textit{PKCS\#12} - PKCS\#12 encoded file, usual extensions are \verb+.pfx+ and \verb+.p12+
+     \item \textit{JKS} - Java KeyStore type file, usual extension is \verb+.jks+
+    \end{itemize}
 
@@
     \end{itemize}
+
 \subsection{License}
 Type of license and possibility of using said tool for testing or production code. 
-Public means that license is not requiered for use in production code but does not mean that it should be used as such.
+    \begin{itemize}
+     \item \textit{Public} - No restrictions for usage, can be used commercialy.
+     \item \textit{Testing} - Tool is free to use non-commercialy. For commercial acquisition of paid license is needed.
+     \item \textit{Paid} - Every type of usage is paid for.
+Restrictive version of product may be available, but to use all the features and be able to use in commercial enviroment paid license is needed.
+    \end{itemize}
+
+Public does not mean that it should be used as such.
 Definition if it is advised to use said tool in production code or only in testing enviroment will be talked about in next chapters under each tool.
@@
 \subsection{Operating Systems}
-In this part the Operating System where the tool is imported is defined.
-Both means that it is implemented under UNIX like systems and Windows systems.
-Otherwise the Operating System is defined (Windows $\vert$ UNIX).
+In this part the Operating System under which the tool is implemented is defined. 
+    \begin{itemize}
+     \item \textit{OS X $\vert$ Windows $\vert$ LINUX} - Tool is implemented under any of the mentioned OS, \verb+LINUX+ defines most common distributions of Linux systems \textit{(Debian or RPM based)}.
+     \item \textit{UNIX} - Tool is implemented under UNIX-like systems, which is same as \textit{OS X $\vert$ LINUX} option.
+     \item \textit{All} - Tool is implemented under every aforementioned operating system.
+    \end{itemize}
 
@@
 \paragraph{Self-signed certificate}
-The tool is capable of generating private key and corresponding self-signed certificate
+Capability of tool to create a self-signed certificate
+\begin{itemize}
+ \item \textit{Yes} - there is a capability of a tool to create self-signed certificate, not necessarily a single command.
+ \item \textit{No} - under no circumstances is it possible to create self-signed certificate using only tool itself.
+\end{itemize}
 
 \paragraph{Certificate Signing Request}
-Possibility of using a command to generate key pair and certificate signing request to certificate authority.
+Capability of tool to create a Certificate Signing Request.
+\begin{itemize}
+ \item \textit{Yes} - The tool is capable of creating a certificate signing request, but does not necessarily generates or packs private key with it.
+ \item \textit{No} - The tool is not capable of creating any type of certificate signing request.
+\end{itemize}
 
 \paragraph{Specify length}
-Possibility to specify the length of output key
+Capability of tool to specify length of created key.
+\begin{itemize}
+ \item \textit{Yes} - changing key length is possible either in fixed range or by declaring required length \textit{(in bits)}.
+ \item \textit{No} - not possible to change key length by any means.
+\end{itemize}
 
 \paragraph{Specify algorithm}
-Possibility to choose between different types of algorithms for key generation and message digest\textit{(hash)}.
+
+\begin{itemize}
+ \item \textit{Yes} - changing key or at least hash algorithm is possible .
+ \item \textit{No} - not possible to change any algorithm by any means.
+\end{itemize}
 
@@
 \paragraph{Specify Type}
-Specify if generated certificate will belong to certificate authority or whether it will be end certificate
+
+\begin{itemize}
+ \item \textit{Yes} - Specification if created certificate will be a certificate authority or end certificate is possible.
+ \item \textit{No} - Created certificate is of fixed type, either end certificate or certificate authority.
+\end{itemize}
 
 \paragraph{Specify Path Length}
-Specify the maximum length of certificate authority chain
+
+\begin{itemize}
+ \item \textit{Yes} - Specification of chain length value is available .
+ \item \textit{No} - The chain length has a fixed value.
+\end{itemize}
+
+\newpage
 
@@
 \paragraph{Certificate Signing Request signing}
-Possibility of signing a certificate signing request with certificate authority's key
+
+\begin{itemize}
+\item \textit{Yes} - The tool supports signing of certificate signing request.
+\item \textit{No} - the tool does not support signing of certificate signing requests.
+\end{itemize}
 
 \paragraph{Create combination of private key and signed chain}
-Possibility of generating private key and chain signed by certificate authority that will be outputed to a single file
+
+\begin{itemize}
+ \item \textit{Yes} - if it is possible to combine private key and corresponding chain into a single file
+ \item \textit{No} - otherwise.
+\end{itemize}
 
 \paragraph{Specify certificate validity}
-{ossibility of choosing how long the certificate will be valid. This should be done by certificate authority.
+
+\begin{itemize}
+ \item \textit{Yes} - Possibility of choosing how long the certificate will be valid. Done by certificate authority.
+ \item \textit{No} - If there is no option to change how long the certificate will be valid, so the duration is a fixed ammount.
+\end{itemize}
 
 \paragraph{Setting Subject Alternative Name for end certificates}
-Possibility of choosing Subject Alternative Name for end certificates. That should be done by IP's or DNS addresses.
+
+\begin{itemize}
+ \item \textit{Yes} - possibility of setting a subject alternative name for certificate. It can be DNS name or IP address.
+ \item \textit{No} - not possible to choose any subject alternative name.
+\end{itemize}
 
 \paragraph{Support for Cryptographic Service Provider}
-Whether the use, choosing and changing of Cryptographic Service Provider is supported.
+\begin{itemize}
+ \item \textit{Yes} - if there is option to change a cryptographic service provider. 
+ \item \textit{No} - the cryptographic service provider canot be changed.
+\end{itemize}
+
+\newpage
 
@@
 \subsubsection{Certificate or certificate chain from a file}
-Possibility of extracting certificate or certificate only from a file. Choice of Yes based on possibility of extracting either from a file.
+\begin{itemize}
+ \item \textit{Yes} - capability of tol to exract certificate or certificate chain from a single file.
+ \item \textit{No} - if extracting is not available.
+\end{itemize}
 
 \subsubsection{Private key only}
-Possibility of extracting private key only from a certificate.
+
+\begin{itemize}
+ \item \textit{Yes} - private key can be exported to a single file.
+ \item \textit{No} - private key extracting is not allowed.
+\end{itemize}
 
 \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
-Possibility of direct conversion (by a command of tested tool) between Java KeyStore and PKCS\#12 type file.
+
+\begin{itemize}
+ \item \textit{Yes} - if tool has a capability to convert Java Keystore to PKCS\#12 file and vica versa.
+ \item \textit{No} - if it doesn't.
+\end{itemize}
 
 \subsection{Importing of certificates and keys into storage files}
-Possibility of importing (additional?) certificates and keys into storage files of said tool. Yes if it is possible to import or add another certificate or key into storage.
+
+\begin{itemize}
+ \item \textit{Yes} - it is possible to import certificates and keys into a tools storage type file \textit{(e. g. PKCS\#12 file)}.
+ \item \textit{No} - it is not possible to import a certificate into a file.
+\end{itemize}
 
@@
 \section{General}
-Tested under Fedora 21, OpenSSL version 1.0.1k-fips
+\textit{Tested under Fedora 21, OpenSSL version 1.0.1k-fips}
   \subsection{Type}
@@
 \begin{displayquote}
-Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.
+\textit{Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.}
 \end{displayquote}
@@
 \begin{displayquote}
-The ca command is quirky and at times downright unfriendly.
-
-The ca utility was originally meant as an example of how to do things in a CA . It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.
-
-The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results. 
+\textit{The ca command is quirky and at times downright unfriendly.}
+
+\textit{The ca utility was originally meant as an example of how to do things in a CA .
+It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.}
+
+\textit{The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.}
+
 \end{displayquote}
@@
 
-Tested under Fedora 21 and OpenSUSE 42.1, openjdk version 1.8.0\_65
+\textit{Tested under Fedora 21 and OpenSUSE 42.1, openjdk version 1.8.0\_65}
 
@@
 
-Tested under Fedora 21, OpenSUSE 42.1, Debian Wheezy, gpgsm (GnuPG) 2.0.29, libgcrypt 1.6.3, libksba 1.3.2 and also MS Windows 10 version 1607 Build 14393.447, MS Windows 8.1 Pro 6.3.9600, gpgsm (GnuPG) 2.0.30 (Gpg4win 2.3.3), libgcrypt 1.6.6, libksba 1.3.4
+\textit{Tested under Fedora 21, OpenSUSE 42.1, Debian Wheezy, gpgsm (GnuPG) 2.0.29, libgcrypt 1.6.3, libksba 1.3.2 and also MS Windows 10 version 1607 Build 14393.447, MS Windows 8.1 Pro 6.3.9600, gpgsm (GnuPG) 2.0.30 (Gpg4win 2.3.3), libgcrypt 1.6.6, libksba 1.3.4}
 
@@
 
-Tested under MS Windows 10 version 1607 Build 14393.447, Keystore Explorer version 5.2.1
+\textit{Tested under MS Windows 10 version 1607 Build 14393.447, Keystore Explorer version 5.2.1}
 
@@
 
-Tested under Windows 10 version 1607 Build 14393.447 and Fedora 21, XCA version 1.3.2 using OpenSSL version 1.0.2d
+\textit{Tested under Windows 10 version 1607 Build 14393.447 and Fedora 21, XCA version 1.3.2 using OpenSSL version 1.0.2d}
 
@@
 You can generate key pair by itself and then use it for generation of certificate.
-If you do not generate key in advance there is option to generate new key whilst generating a certificate.\textit{{Figure 6.1}} To generate a certificate click on Certificates tab and press New Certificate.
-There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm (\verb+MD5|SHA1|SHA224|SHA256|SHA384|SHA512|RIPEMD160+).
-What must be changed is default hash function because it is set to SHA-1 which is no longer considered safe.
+If you do not generate key in advance there is option to generate new key whilst generating a certificate.\textit{{Figure 6.1}}  \\
+
+To generate a certificate click on Certificates tab and press New Certificate. There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm.  \\
+
+Hash algorithm is one of: \verb+MD5, SHA1, SHA224, SHA256, SHA384, SHA512, RIPEMD160+. It needs to be changed because hash function is set to SHA-1 which is no longer considered safe.  \\
+
 Under Subject tab, you shoose Common Name, Organisation, etc.
@@
 \textit{(Figure 6.2)}
+
 \begin{figure}[!ht]
@@
 
-Tested under Fedora 21, certtool version 3.3.16
+\textit{Tested under Fedora 21, certtool version 3.3.16}
 
@@
 
-Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298
+\textit{Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298}
 
@@
 
-Tested under MS Windows 10 version 14393.447
+\textit{Tested under MS Windows 10 version 14393.447}
 
@@
 
-The main thing to understand is, that every tool has had its strong and weak points.
-Every should be used in complience with required properties of use.
-That can mean restrictions on used Operating System (e.g.
-customer has only access to Apple computers with OS X operating system), or for example restrictions how it should be used on Operating System (command line vs GUI programm).
+The main thing to understand is, that every tool has had its strong and weak points. Every should be used in complience with required properties of use.\\
+
+That can mean restrictions on used Operating System \textit{(e.g.
+customer has only access to Apple computers with OS X operating system)}, or for example restrictions how it should be used on Operating System \textit{(command line vs GUI programm)}.
 In the next part i will try to go over strengths and weaknesses of each tool that I have tested.
@@
 It is a great command line tool, can work with PEM, DES and PKCS\#12 files.
-Strong point is a easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in man pages and also a O'REILLY's OpenSSL book.
+Strong point is a easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in man pages and also a O'REILLY OpenSSL book.
 Another strong point is configuration, which can be done in file. I tested it with creation of appropriate directories and configs.
@@
 
-Main downfall is that keys of length greater than 4096 take longer to generate (notably RSA of length 16192, it took almost 2 hours to generate).
+Main downfall is that keys of length greater than 4096 take longer to generate \textit{(notably RSA of length 16192, it took almost 2 hours to generate)}.
 
@@
 Great support for different key and hash algorithm types.
-Supports key lengths of higher values (greater than 4096 RSA for example).
+Supports key lengths of higher values \textit{(greater than 4096 RSA for example)}.
 Its weaknesses are no support for CSP and availibility only under UNIX like Operating Systems.
@@
 
+\section{Choosing the right tool}
+The crucial part of deciding which tool to use is to know what is desired. The first choice to make is to decide what file type will be required.
+In this list there are most useful tools for each type:
+
+\begin{itemize}
+ \item \textbf{PKCS\#12} \begin{enumerate}\item \textit{GUI} - XCA \item \textit{Command Line} - OpenSSL \end{enumerate}
+ \item \textbf{Java KeyStore} \begin{enumerate}\item \textit{GUI} - Keystore Explorer \item \textit{Command Line} - keytool \end{enumerate}
+\end{itemize}
+
+Other tested tools can be also used, but \textit{OpenSSL, Keytool, XCA} and \textit{Keystore Explorer} can do almost everything, along with their ease of use.
+My personal favourite has became \textit{XCA} as it is tool where i checked if information about certificates from other tools checked out.\\
+
+But only because they can do everything doesn't mean they are best at everything, for example if self-signed certificate is neede only for testing purposes, one can be really quickkly made with help Windows PowerShell PKI Module where no additional instalations are required.\\
+
+Considering Java KeyStore tools, only 2 were tested, 1 GUI and 1 Command Line. Nevertheless, even though they have their own upsides and downsides, are easy and quickly ready to use.\\
+
 \end{document}

### 2016-11-29 TEX/draft.tex
Minor changes, mostly format of text, needed to change OpenSSL General, check again keystore expl/keytool and GnuTLS.

@@
 
-\title{Review and comparison of tools for manageing X.509 type keys and certificates}
+\title{Review and comparison of tools for managing X.509 type keys and certificates}
 \author{Oliver Bodnár}
@@
 Primary goal of this work is to compare and review some of the basic functionalities \textit{(e.g.
-generation of keys and certificates, ability to create a certificate signing request,...)} of tools working with keys and certificates in X509 public key infrastructure.
+generation of keys and certificates, ability to create a certificate signing request,...)} of tools working with keys and certificates in X.509 public key infrastructure.
 Comparison of tools is necessary to understand that ability of a tool to do everything that was tested does not mean that it is the best tool to use in every situation.
@@
 GnuTLS                        & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}UNIX            & Command Line        \\ \hline
-Makecert                      & PKCS12 & \cellcolor[HTML]{FE0000}No			    & Public  & \cellcolor[HTML]{FFC702}Windows         & Command Line        \\ \hline
+Makecert and pvk2pfx          & PKCS12 & \cellcolor[HTML]{FE0000}No			    & Public  & \cellcolor[HTML]{FFC702}Windows         & Command Line        \\ \hline
 Windows PowerShell PKI Module & PKCS12 & \cellcolor[HTML]{34FF34}Yes			    & Public  & \cellcolor[HTML]{FFC702}Windows         & Command Line        \\ \hline
@@
 GnuTLS                        & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
-Makecert                      & \cellcolor[HTML]{34FF34}Yes					     & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFC702}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
+Makecert and pvk2pfx          & \cellcolor[HTML]{34FF34}Yes					     & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FFC702}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
 Windows PowerShell PKI Module & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
@@
 GnuTLS                        & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{FE0000}No               & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
-Makecert	              & \cellcolor[HTML]{FE0000}No    & \cellcolor[HTML]{FE0000}No	 	 & \cellcolor[HTML]{34FF34}Yes	               & \cellcolor[HTML]{FE0000}No                 & \cellcolor[HTML]{34FF34}Yes              		                          \\ \hline
+Makecert and pvk2pfx          & \cellcolor[HTML]{FE0000}No    & \cellcolor[HTML]{FE0000}No	 	 & \cellcolor[HTML]{34FF34}Yes	               & \cellcolor[HTML]{FE0000}No                 & \cellcolor[HTML]{34FF34}Yes              		                          \\ \hline
 Windows PowerShell PKI Module & \cellcolor[HTML]{FE0000}No    & \cellcolor[HTML]{FE0000}No	         & \cellcolor[HTML]{34FF34}Yes	               & \cellcolor[HTML]{34FF34}Yes	            & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
@@
 \section{General}
-\textit{Tested under Fedora 21, OpenSSL version 1.0.1k-fips}
+\textit{Tested under Fedora 21, OpenSSL version 1.0.1k-fips} %DOPLNIT INFO O CNF FILE
   \subsection{Type}
   OpenSSL uses PKCS12 to store keys and certificates.
-Certificates and keys generated in OpenSSL are however being made into PEM or DER encoded file.
+Certificates and keys generated in OpenSSL are being made into PEM or DER encoded file.
 PEM or DER encoded keys and certificates can then be stored inside single PKCS\#12 file.
@@
 
-However for any other type of Key generating algorithm, it is better to create key separately. There are options to create a key in onecommand, but they are quirky.
+However for any other type of Key generating algorithm, it is better to create key separately. There are options to create a key in one command, but they are quirky.
 
@@
       \paragraph{Specify path length}
-Specifying of path length is made by setting a \verb+<maxChainLengthInteger>+ to desired value (e.g. if generated certificate should be used only for generating end certificates the value is 0)
+Specifying of path length is made by setting a \verb+<maxChainLengthInteger>+ to desired value (e.g. if generated certificate/key should be used only for signingend certificates the value is 0)
   \subsection{Specifications}
@@
   \subsection{View and information}
-When viewing certificates, command for PEM and DER certificates will return errors with command for PKCS\#12 amd JKS files.
+When viewing certificates, command for PEM and DER certificates will return errors with command for PKCS\#12 and JKS files.
 
@@
 
-Keytool natively supports only DSA of length in between 512 and 1024, and is considered to be dangerous to use. RSA with key length of at least 2048 is preffered.
+Keytool natively supports only DSA of length in between 512 and 1024, and is considered to be dangerous to use. RSA with key length of at least 2048 is preferred.
 
@@
       \paragraph{Specify path length}
-Specifying of path length is possible while making a certificate by using  \\
+Specifying path length is possible while making a certificate by using  \\
 \verb+-ext BC=pathlen:[int path length]+ option.
@@
 
+GnuPG is unable to do anything besides creating a certificate signing request in X.509 public key infrastructure
+
 \chapter{Keystore Explorer}
@@
   \subsection{Importing certificates and keys into storage files}
-It is possible to import a certificates and keys by chosing Import option.
+It is possible to import certificates and keys by chosing Import option.
 
@@
   \subsection{License}
-XCA is distributed under BSD License - it is free to use for testing and also commercialy.
+XCA is distributed under BSD License - it is free to use for testing and also commercially.
 
@@
     \subsubsection{Specify certificate validity}
-Time period during which is a certificate valid is defined under Extensions tab.
+Time period during which a certificate is valid is defined under Extensions tab.
     \subsubsection{Setting Subject Alternative Name for end certificates}
-Subject Alternative Names are specified in appropriate section under a Extensions tab.
+Subject Alternative Names are specified in appropriate section under an Extensions tab.
 \textit{(Figure 6.5)}
@@
   \subsection{License}
-GnuTLS is under Gnu Public License \- free to use commercialy.
+GnuTLS is under Gnu Public License \- free to use commercially.
 
@@
 More options when generating self-signed certificate (or a CSR) you need to create a config file which has structure as is in appendix \textit{GnuTLS.cfg} 
-For whole list of options in a config file look up \verb+man certtol+.
+For whole list of options in a config file look up \verb+man certtool+.
 
@@
 
-To define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512]+ option while generating a certificate.
-
       \paragraph{Specify algorithm}
 Algorithm for key generation is specified in \verb+--[rsa|dsa|ecc]+ option where rsa = RSA, dsa = DSA, ecc = ECDSA.
+
+To define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512]+ option while generating a certificate.
 
@@
 
-\chapter{Makecert}
+\chapter{Makecert and pvk2pfx}
 
@@
 
-\textit{Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298}
+\textit{Tested under MS Windows 10 version 14393.447, makecert.exe version 6.3.9600.17298} \\
+Makecert is deprecated by Microsoft itself as cited on MSDN MakeCert site.
 
@@
 In addition to use the tool you need to start a Developer Command Prompt for Visual Studio (on Windows 10).
-\\ 
-In addition to that makecert is deprecated itself as cited on MSDN MakeCert site.
+
   \subsection{License}
@@
       \paragraph{Specify algorithm}
-To specify hash algorithm use \verb+-a [sha256|sha384|sha512]+ option. Supported are also SHA1 and MD5 but those are considered unsafe.
+To specify hash algorithm use \verb+-a [sha256|sha384|sha512]+ option. Supported are also SHA1 and MD5 but those are considered insecure.
 
@@
   \subsection{Importing certificates and keys into storage files}
-For importing of keys and certificates into PKCS\#12 file, use pvk2pfx as in generating self-signed part. There is just option to add 1 certificate and 1 private key into a file.
+For importing of keys and certificates into PKCS\#12 file, use \verb+pvk2pfx+ as in generating self-signed part. There is just option to add 1 certificate and 1 private key into a file.
 
@@
 
-This commands howeve shows only thumbprint of certificate and a \verb+dns.name+. 
+This commands however show only thumbprint of certificate and a \verb+dns.name+. 
   \subsection{License}
@@
   \subsection{Importing certificates and keys into storage files}
-It is possible as exporting a certificate into PKCS\#12 file.
+It is possible in a simmilar way as exporting a certificate into PKCS\#12 file.
+Only difference is that all certificates that should be imported into a single folder and then \verb+<path>+ should be set to that directory.
 
@@
 That can mean restrictions on used Operating System \textit{(e.g.
-customer has only access to Apple computers with OS X operating system)}, or for example restrictions how it should be used on Operating System \textit{(command line vs GUI programm)}.
+customer has only access to Apple computers with OS X operating system)}, or for example restrictions how it should be used on Operating System \textit{(command line vs GUI program)}.
 In the next part i will try to go over strengths and weaknesses of each tool that I have tested.
@@
 \section{OpenSSL}
-It is a great command line tool, can work with PEM, DES and PKCS\#12 files.
-Strong point is a easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in man pages and also a O'REILLY OpenSSL book.
+It is a great command line tool, can work with PEM, DER and PKCS\#12 files.
+Strong point is an easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in manual pages and also a O'REILLY OpenSSL book.
 Another strong point is configuration, which can be done in file. I tested it with creation of appropriate directories and configs.
@@
 By default the CSP is \verb+java.security.provider+ which allows RSA and DSA options and SHA-1,MD5,SHA-256 and SHA-512 hash algorithms.
-This Changes when choosing other Cryptographic Service Provider.
+This changes when choosing other Cryptographic Service Provider.
 Working with it is quite easy and support for exporting as PKCS\#12 is usefull addition.
@@
 \section{Keystore Explorer}
-A great GUI tool for when you need to work with different types of Java Keystore files for example supports Bouncy Castle implementation.
+A great GUI tool for when you need to work with different types of Java Keystore files.
+For example, Keystore Explorer supports Bouncy Castle implementation.
 Even though CSP support is not implicit, there are different choices already implemented.
@@
 XCA is a great GUI tool that can work with PEM, DER and PKCS\#12 type of files.
-Main advantage is simplicity and ammount of options, basic options are readily availiable as a button.
+Main advantage is simplicity and amount of options, basic options are readily availiable as a button.
 There are many exporting options, for example PEM encoded certificate file with PKCS\#8 encrypted key file.
@@
 
-\section{Choosing the right tool}
+\chapter{Choosing the right tool}
 The crucial part of deciding which tool to use is to know what is desired. The first choice to make is to decide what file type will be required.
@@
 Other tested tools can be also used, but \textit{OpenSSL, Keytool, XCA} and \textit{Keystore Explorer} can do almost everything, along with their ease of use.
-My personal favourite has became \textit{XCA} as it is tool where i checked if information about certificates from other tools checked out.\\
-
-But only because they can do everything doesn't mean they are best at everything, for example if self-signed certificate is neede only for testing purposes, one can be really quickkly made with help Windows PowerShell PKI Module where no additional instalations are required.\\
+My personal favourite has become \textit{XCA} as it is a tool where I confirmed if information about certificates from other tools was as expected.\\
+
+But only because they can do everything doesn't mean they are best at everything, for example if self-signed certificate is needed only for testing purposes, one can be really quickly made with the help of Windows PowerShell PKI Module where no additional instalations are required.\\
 

### 2016-12-01 TEX/draft.tex
Only Keystore Explorer is left

@@
 \textit{Tested under Fedora 21, OpenSSL version 1.0.1k-fips} %DOPLNIT INFO O CNF FILE
+
+OpenSSL heavily relies on a configuration file that needs to be prepared along with a default directory sequence in advance.
+Hierarchy of that directory sequence can be seen in supplied OpenSSL.cnf file under \verb+[ CA_default ]+ part.
+
+Time how long the certificate will be valid can be given in csr but only as a suggestion. Ultimately the real time of
+validity is always given by CA signing the CSR.
+
   \subsection{Type}
@@
   \subsection{License}
-OpenSSL is free to use commercialy, however creating CA is not advised in O'REILLY's Network Security with OpenSSL by J. Viega, M. Messier and P. Chandra on page 59,
-\begin{displayquote}
-\textit{Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.}
-\end{displayquote}
-and also hinted in manual pages:
-\begin{displayquote}
-\textit{The ca command is quirky and at times downright unfriendly.}
-
-\textit{The ca utility was originally meant as an example of how to do things in a CA .
-It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.}
-
-\textit{The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.}
-
-\end{displayquote}
-
+OpenSSL is free to use commercialy. Full text is available at \url{https://www.openssl.org/source/license.html}  
 \section{Generation and signing of certificates}
@@
     \subsubsection{Specify certificate validity}
-    Time how long the certificate will be valid can be given in csr but only as a suggestion. Ultimately the real time of validity is always given by CA signing the CSR.
+    Time how long the certificate will be valid is chosen by CA during signing the CSR, where in command for signing certificate signing request we choose desired duration in days by changing \verb+-days <velidity_time>+ part.
+
     \subsubsection{Setting Subject Alternative Name for end certificates}
@@
     \subsubsection{Certificate Signing Request signing}
-Possible %but i need to look wy it does not work for me
-    \subsubsection{Create combination of private key and signed chain}
-When you create a certificate by signing a request to sign key only, you can validate chain. %but i think that is not what is regarded here as signed chain    
+Possible by command:
+\begin{verbatim}
+certtool --generate-certificate --load-request <csr_file> \
+         --load-ca-certificate <path_to_ca_cert> \
+         --load-ca-privkey <ca_cert_privkey_file> 
+         --outfile <name>.pem
+\end{verbatim}
+
     \subsubsection{Specify certificate validity}
@@
 
-    \subsubsection{Certificate or certificate chain from a file}
-
     \subsubsection{Private key only}
@@
   \subsection{Importing certificates and keys into storage files}
-Possible.
+To import certificate and key into a PKCS\#12 file use command:
+\begin{verbatim}
+certtool --load-certificate <in_cert> \
+         --load-privkey <in_key> \
+         --to-p12 --outder --outfile <name>.[p12|pfx]
+\end{verbatim}
 
@@
 It is a great command line tool, can work with PEM, DER and PKCS\#12 files.
-Strong point is an easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in manual pages and also a O'REILLY OpenSSL book.
-Another strong point is configuration, which can be done in file. I tested it with creation of appropriate directories and configs.
+Strong point is an easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal -  creating CA is not advised in O'REILLY's Network Security with OpenSSL by J.
+Viega, M.
+Messier and P.
+Chandra on page 59,
+\begin{displayquote}
+\textit{Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.}
+\end{displayquote}
+and also hinted in manual pages:
+\begin{displayquote}
+\textit{The ca command is quirky and at times downright unfriendly.}
+
+\textit{The ca utility was originally meant as an example of how to do things in a CA .
+It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.}
+
+\textit{The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.}
+
+\end{displayquote}
+
+On the other hand strong point of OpenSSL is configuration of created certificate, which can be done in file. I tested it with creation of appropriate directories and configs.
 

### 2016-12-01 TEX/draft.tex
Changed everything what we talked about today

@@
 
-\title{Review and comparison of tools for managing X.509 type keys and certificates}
+\title{Review and comparison of tools for managing X.509 certificates and keys}
 \author{Oliver Bodnár}
@@
 
-\begin{itemize}
-\item \textit{Yes} - The tool supports signing of certificate signing request.
-\item \textit{No} - the tool does not support signing of certificate signing requests.
-\end{itemize}
+\textit{Yes} means that the tool supports signing of certificate signing request. \textit{No} if it does not support signing of certificate signing requests.
 
@@
 
-\begin{itemize}
- \item \textit{Yes} - if it is possible to combine private key and corresponding chain into a single file
- \item \textit{No} - otherwise.
-\end{itemize}
+\textit{Yes} if it is possible to combine private key and corresponding chain into a single file, \textit{No} - otherwise.
 
@@
 
-\begin{itemize}
- \item \textit{Yes} - Possibility of choosing how long the certificate will be valid. Done by certificate authority.
- \item \textit{No} - If there is no option to change how long the certificate will be valid, so the duration is a fixed ammount.
-\end{itemize}
+\textit{Yes} - Possibility of choosing how long the certificate will be valid.
+Done by certificate authority.
+\textit{No} - If there is no option to change how long the certificate will be valid, so the duration is a fixed ammount.
+
+Time how long the certificate will be valid can be given in csr but only as a suggestion. Ultimately the real time of
+validity is always given by CA signing the CSR.
 
@@
       \paragraph{Specify path length}
-Specifying of path length is made by setting a \verb+<maxChainLengthInteger>+ to desired value (e.g. if generated certificate/key should be used only for signingend certificates the value is 0)
+Specifying of path length is made by setting a \verb+<maxChainLengthInteger>+ to desired value (e.g. if generated certificate/key should be used only for signing end certificates the value is 0)
   \subsection{Specifications}
@@
 \end{verbatim}
-    It should be mentioned that if there are multiple certificates in a chain they are all going to be in same output file.
+    It should be noted that if there are multiple certificates in a chain they are all going to be in same output file.
 
@@
 \end{verbatim}
+
+\section{Note}
+However using self-signed certificate made with \verb+ca+ option as CA certificates is not ideal -  creating CA is not advised in O'REILLY's Network Security with OpenSSL by J.
+Viega, M.
+Messier and P.
+Chandra on page 59,
+\begin{displayquote}
+\textit{Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.}
+\end{displayquote}
+and also hinted in manual pages:
+\begin{displayquote}
+\textit{The ca command is quirky and at times downright unfriendly.}
+
+\textit{The ca utility was originally meant as an example of how to do things in a CA .
+It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.}
+
+\textit{The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.}
+
+\end{displayquote}
 
@@
 Possible by using \verb+gpgsm --gen-key > <output_file>+ command, but private key is not a part of output CSR.     
-
-GnuPG is unable to do anything besides creating a certificate signing request in X.509 public key infrastructure
+\section{Note}
+GnuPG is unable to do anything besides creating a certificate signing request in X.509 public key infrastructure, that does not include a private key within itself.
 
@@
 Keystore Explorer supports both Java Keystore and PKCS\#12 type files, in addition it has a support for alternatives to JKS such as JCEKS, BKS, BKS-V1, UBER.
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Choosing type}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Generating keys}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Generating certificate}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Generating a CSR}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Basic Constraints}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Signing of a CSR}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Generation of key for new cert}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Specify usage}
@@
 Certificate Signing Request is generated similarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Generation of CSR}
@@
 Algorithm used for key generation is specified during generation of keys (\verb+RSA|DSA|EC+).
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Specifying of length and algorithm used}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
  \caption{Basic constraints, validity and SAN}
@@
 If not you need to generate new key pair, then use export option to export private part of a key, delete key pair from database and then import private key.
-to create a combination, simply generate new certificate while using said private key.
+To create a combination, simply generate new certificate while using said private key.
+
+To export certificate with private key and certificate chain, simply use Export option under \textit{Certificates} tab.
+There you can choose if you wish to export it in a single \textit{PKCS\#12} type file or certificate and key separately, PEM encoded.
+
     \subsubsection{Specify certificate validity}
@@
     \subsubsection{Private key only}
-Private key is stored and generated while generating a certificate but the type .pvk is uncommon.
+Private key is stored and generated while generating a certificate but the type .pvk is uncommon. It is Microsoft's own key storage type more on \url{http://www.drh-consultancy.demon.co.uk/pvk.html}
 
@@
 \section{OpenSSL}
-It is a great command line tool, can work with PEM, DER and PKCS\#12 files.
-Strong point is an easy form of creating a self-signed certificate, however using it for CA certificates with ca option is not ideal -  creating CA is not advised in O'REILLY's Network Security with OpenSSL by J.
-Viega, M.
-Messier and P.
-Chandra on page 59,
-\begin{displayquote}
-\textit{Since OpenSSL's command-line CA functionality was intended primarely as an example of how to use OpenSSL to build a CA, we don't recommend that you attempt to use it in a large production environment.}
-\end{displayquote}
-and also hinted in manual pages:
-\begin{displayquote}
-\textit{The ca command is quirky and at times downright unfriendly.}
-
-\textit{The ca utility was originally meant as an example of how to do things in a CA .
-It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.}
-
-\textit{The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.}
-
-\end{displayquote}
+It is a great command line tool, can work with PEM, DER and PKCS\#12 files. Strong point is a easy form of
+creating a self-signed certificate, however using it for CA certificates with ca option is not ideal - it is noted in man
+pages and also a O’REILLY OpenSSL book.
 

### 2016-12-02 TEX/draft.tex
Changed itemized list into fluent text in Specifications

@@
 
-\textit{Yes} means that the tool supports signing of certificate signing request. \textit{No} if it does not support signing of certificate signing requests.
+\textit{Yes} means that the tool supports signing of certificate signing request. \textit{No} if it does not.
 
@@
 
-\textit{Yes} - Possibility of choosing how long the certificate will be valid.
-Done by certificate authority.
-\textit{No} - If there is no option to change how long the certificate will be valid, so the duration is a fixed ammount.
+\textit{Yes} if there is possibility of choosing how long the certificate will be valid. Done by certificate authority. \textit{No} If there is not such an  option, so the duration is a fixed ammount.
 
@@
 
-\begin{itemize}
- \item \textit{Yes} - possibility of setting a subject alternative name for certificate. It can be DNS name or IP address.
- \item \textit{No} - not possible to choose any subject alternative name.
-\end{itemize}
+\textit{Yes} means a  possibility of setting a subject alternative name for certificate. It can be DNS name or IP address. \textit{No} if there is no option to change any alternative name.
 
 \paragraph{Support for Cryptographic Service Provider}
-\begin{itemize}
- \item \textit{Yes} - if there is option to change a cryptographic service provider. 
- \item \textit{No} - the cryptographic service provider canot be changed.
-\end{itemize}
+\textit{Yes} if there is option to change a cryptographic service provider. \textit{No} means that the cryptographic service provider canot be changed.
 

### 2017-01-11 TEX/draft.tex
Final, added key length to GnuPG and Sources

@@
 Keytool                       & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
-GnuPG                         & \cellcolor[HTML]{FE0000}No                                           & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000} No & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
+GnuPG                         & \cellcolor[HTML]{FE0000}No                                           & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{FE0000}No  \\ \hline
 Keystore explorer             & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
@@
 GnuPG is unable to do anything besides creating a certificate signing request in X.509 public key infrastructure, that does not include a private key within itself.
-
+	\paragraph{Specify Length}
+While choosing of key length is avaliable in GnuPG, using \verb+4096bit+ length freezes gpgsm. \verb+2048bit+ and \verb+1024bit+ is however fine.
 \chapter{Keystore Explorer}
@@
 
+\chapter{Sources}
+For all of the tools where manual pages or help command were avaliable I used them. Besize that I used only a couple of documents and websites: 
+\begin{itemize}
+ \item \textbf{General} 
+   \begin{enumerate}
+    \item \href{https://tools.ietf.org/rfc/rfc5280.txt}{RFC 5280}
+    \item \href{https://books.google.cz/books/about/Digital_Certificates.html?id=0_3XAAAAMAAJ}{Digital Certificates: Applied Internet Security}
+   \end{enumerate}
+
+ \item \textbf{OpenSSL} 
+    \begin{enumerate} 
+      \item Manual Pages \verb+man <command || option>+
+      \item \href{http://operational.io/openssl-commonly-used-commands/}{List of most used OpenSSL commands}
+      \item \href{https://jamielinux.com/docs/openssl-certificate-authority/index.html}{Basic tutorial on establishing CA structure}
+      \item \href{https://books.google.cz/books?id=IIqwAy4qEl0C&pg=PT4&lpg=PT4&dq=978-0-596-00270-1&source=bl&ots=mb74-Q3DXs&sig=RDQA26zKltVYA1_5PTSkd2tk-Ag&hl=sk&sa=X&ved=0ahUKEwj-mcT4wLrRAhWbIFAKHQcDAaYQ6AEIGTAA#v=onepage&q=978-0-596-00270-1&f=false}{Network Security with OpenSSL By John Viega, Matt Messier, Pravir Chandra}
+    \end{enumerate}
+ \item{Keytool}
+    \begin{enumerate}
+     \item \href{http://docs.oracle.com/javase/7/docs/technotes/tools/solaris/keytool.html}{Documentation to keytool from Oracle}
+    \end{enumerate}
+ \item{GnuPG}
+  \begin{enumerate}
+   \item \verb+gpgsm --help+ option
+   \item \href{https://lists.gnupg.org/pipermail/gnupg-devel/2011-March/025989.html}{Public mailing list}
+  \end{enumerate}
+ \item{Keystore Explorer}
+  \begin{enumerate}
+   \item \href{http://help.farnedi.it/wp-content/uploads/2014/08/Generate_Keystore_with_KeyStore_Explorer.pdf}{Keystore Generating Tutorial}
+  \end{enumerate}
+ \item{XCA}
+  \begin{enumerate}
+   \item \href{http://xca.sourceforge.net/xca.html}{XCA Sourceforge guide and options}
+  \end{enumerate}
+ \item{GnuTLS}
+  \begin{enumerate}
+   \item \href{https://www.gnutls.org/manual/html_node/certtool-Invocation.html}{GnuTLS manual}
+  \end{enumerate}
+ \item{Makecert and pvk2pfx}
+  \begin{enumerate}
+   \item \href{https://msdn.microsoft.com/en-us/library/windows/desktop/aa386968(v=vs.85).aspx}{Microsoft's Makecert MSDN page}
+   \item \href{https://msdn.microsoft.com/en-us/library/bfsktky3(VS.100).aspx}{Microsoft page dedicated to use of Makecert.exe}
+   \item \href{https://blog.jayway.com/2014/09/03/creating-self-signed-certificates-with-makecert-exe-for-development/}{Tutorial on creating self-signed certificate with makecert}
+  \end{enumerate}
+ \item{Windows PowerShell PKI Module}
+  \begin{enumerate}
+   \item \href{https://technet.microsoft.com/en-us/library/hh848633.aspx}{Microsoft's page on New-SelfSignedCertificate}
+   \item \href{http://windowsitpro.com/blog/creating-self-signed-certificates-powershell}{Tutorial on creating self-signed certificate via PowerShell}
+   \item \href{http://woshub.com/how-to-create-self-signed-certificate-with-powershell/}{Another tutorial on creating self-signed certificate}
+  \end{enumerate}
+
+\end{itemize}
+
 \end{document}
